### 2020-10-10 conference_101719.tex
edit title and authors

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Community Embeddings for Friend Suggestions\\
    \thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{
    \IEEEauthorblockN{Anton I. N. Begehr}
    \IEEEauthorblockA{
        \textit{Graduate School of Business}\\
        \textit{National Research University Higher School of Economics}\\
        Moscow, Russia\\
        a.begehr@fu-berlin.de\\
    }
    \and
    \IEEEauthorblockN{Prof. Dr. Petr Panfilov}
    \IEEEauthorblockA{
        \textit{Graduate School of Business}\\
        \textit{National Research University Higher School of Economics}\\
        Moscow, Russia\\
        ppanfilov@hse.ru\\
    }
}

\maketitle

\begin{abstract}
    This document is a model and instructions for \LaTeX.
    This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes,
    or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
    component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins,
column widths, line spaces, and text fonts are prescribed; please do not
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement
and others are deliberate, using specifications that anticipate your paper
as one part of the entire proceedings, and not as an independent document.
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a
separate text file. Complete all content and organizational editing before
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been
formatted and styled. Do not number text heads---{\LaTeX} will do that
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text,
even after they have been defined in the abstract. Abbreviations such as
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
    \item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
    \item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
    \item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
    \item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your
equations more compact, you may use the solidus (~/~), the exp function, or
appropriate exponents. Italicize Roman symbols for quantities and variables,
but not Greek symbols. Use a long dash rather than a hyphen for a minus
sign. Punctuate equations with commas or periods when they are part of a
sentence, as in:
\begin{equation}
    a+b=\gamma\label{eq}
\end{equation}

Be sure that the
symbols in your equation have been defined before or immediately following
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

    {\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

    {\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
    \item The word ``data'' is plural, not singular.
    \item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
    \item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
    \item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
    \item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
    \item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
    \item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
    \item Do not confuse ``imply'' and ``infer''.
    \item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
    \item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
    \item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A
minimum of one author is required for all conference articles. Author names
should be listed starting from left to right and then moving down to the
next line. This is the author sequence that will be used in future citations
and by indexing services. Names should not be listed in columns nor group by
affiliation. Please keep your affiliations as succinct as possible (for
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not
topically subordinate to each other. Examples include Acknowledgments and
References and, for these, the correct style to use is ``Heading 5''. Use
``figure caption'' for your Figure captions, and ``table head'' for your
table title. Run-in heads, such as ``Abstract'', will require you to apply a
style (in this case, italic) in addition to the style provided by the drop
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For
example, the paper title is the primary text head because all subsequent
material relates and elaborates on this one topic. If there are two or more
sub-topics, the next level head (uppercase Roman numerals) should be used
and, conversely, if there are not at least two sub-topics, then no subheads
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and
bottom of columns. Avoid placing them in the middle of columns. Large
figures and tables may span across both columns. Figure captions should be
below the figures; table heads should appear above the tables. Insert
figures and tables after they are cited in the text. Use the abbreviation
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
    \caption{Table Type Styles}
    \begin{center}
        \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Table} & \multicolumn{3}{|c|}{\textbf{Table Column Head}}                                                         \\
            \cline{2-4}
            \textbf{Head}  & \textbf{\textit{Table column subhead}}           & \textbf{\textit{Subhead}} & \textbf{\textit{Subhead}} \\
            \hline
            copy           & More table copy$^{\mathrm{a}}$                   &                           &                           \\
            \hline
            \multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
        \end{tabular}
        \label{tab1}
    \end{center}
\end{table}

\begin{figure}[htbp]
    \centerline{\includegraphics{fig1.png}}
    \caption{Example of a figure caption.}
    \label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words
rather than symbols or abbreviations when writing Figure axis labels to
avoid confusing the reader. As an example, write the quantity
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including
units in the label, present them within parentheses. Do not label axes only
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of
quantities and units. For example, write ``Temperature (K)'', not
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B.
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at
the bottom of the column in which it was cited. Do not put footnotes in the
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use
``et al.''. Papers that have not been published, even if they have been
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers
that have been accepted for publication should be cited as ``in press'' \cite{b5}.
Capitalize only the first word in a paper title, except for proper nouns and
element symbols.

For papers published in translation journals, please give the English
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
    \bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
    \bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
    \bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
    \bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
    \bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
    \bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
    \bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2020-10-11 conference_101719.tex
abstract and keywords

@@
 \begin{abstract}
-    This document is a model and instructions for \LaTeX.
-    This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes,
-    or Math in Paper Title or Abstract.
+    Graphs, such as social networks, emerge naturally from various real-world situations. Recently, graph embedding methods have gained traction in data science research.
+    Recommender systems are used in a wide range of business applications and are essential for online e-business models to survive and strive in the contemporary market.
+Using graph embeddings for recommendation tasks, have the possibility of improving upon recommender systems, because of data compression, their feature vector format, and sub-quadratic time complexity.
+    Graph and community embeddings generated with ComE BGMM+VI are used to build a recommender system for friend suggestions.
+ComE BGMM+VI is an alteration of the community embeddings algorithm ComE.
+ComE BGMM+VI applies a Bayesian Gaussian mixture model and variational inference for community embedding and detection.
+    Recommendations are evaluated by the top-N hit-rate over users with at least 50 friends.
+A friend suggestions recommender system with a top-10 leave-one-out hit-rate of 43.6\% and run-time optimized 32.9\% is presented.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-    component, formatting, style, styling, insert
+    graph, embedding, community embedding, recommendations, friend suggestions
 \end{IEEEkeywords}

### 2020-10-11 conference_101719.tex
add comma

@@
     Graphs, such as social networks, emerge naturally from various real-world situations. Recently, graph embedding methods have gained traction in data science research.
-    Recommender systems are used in a wide range of business applications and are essential for online e-business models to survive and strive in the contemporary market.
+    Recommender systems are used in a wide range of business applications and are essential for online, e-business models to survive and strive in the contemporary market.
 Using graph embeddings for recommendation tasks, have the possibility of improving upon recommender systems, because of data compression, their feature vector format, and sub-quadratic time complexity.

### 2020-10-11 conference_101719.tex
add intro

@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
+
+Graphs, such as social networks, knowledge graphs, content-rating graphs, and communication networks, emerge naturally from various real-world situations.
+Analyzing these graphs leads to findings and understanding of the underlying structures, coherences, and dependencies.
+Recently, methods for embedding graph's nodes into lower-dimensional Euclidean spaces, called graph embeddings, have gained traction in multiple areas of data science research.\cite{Goyal_2018}
+
+Due to the rapid growth of the internet and data accumulation, recommender systems are essential for e-business and online business models to survive and strive in the contemporary market.\cite{Polatidis2013RecommenderST} Modern recommender systems need to take into account the huge amounts of user data generated at all times in big data systems around the world and improve recommendations instead of failing under the thrust of big data overload.
+
+Utilizing graph embeddings for recommendation tasks, has recently gained research traction.\cite{Palumbo2018AnEC, Palumbo2018KnowledgeGE, GradGyenge2017GraphEB, Sathish2019GraphEB} Advantages of graph embeddings include data compression and the Euclidean feature vector format.\cite{Godec2018} Given these advantages and provided competitive results, graph embeddings have the possibility of greatly improving upon graph-based use-cases like recommender systems.
+
+Community Embeddings, in addition to embedding a graph's nodes through first- and second-order proximity, also preserve higher-order proximity by embedding clusters present in the graph data.
+The graph and community embedding algorithm ComE aims to preserve first-, second- and higher-order proximity by embedding a graph's nodes and communities.\cite{ComE}
+
+This work specifically examines community embeddings for friend suggestion recommender systems and evaluates recommendations on social network graph data for the use-case of friend suggestions.
+Graph and community embeddings generated with ComE BGMM+VI are used to develop a friend suggestions recommender system.
+Recommendations are evaluated by the top-$N$ recommendations hit-rate of test edges.
+A friend suggestions recommender system with a top-$10$ leave-one-out hit-rate of over $40\%$ is reached.
 

### 2020-10-11 conference_101719.tex
use bibtex and add literature from MT

--- 2020-10-11 conference_101719.tex
@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{textcomp}
-\usepackage{xcolor}
+\usepackage[style=numeric, backend=bibtex, language=english, maxbibnames=99]{biblatex}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
+\emergencystretch=8em
+
+\bibliography{literature}
+
 \begin{document}
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
+
+Graphs, such as social networks, knowledge graphs, content-rating graphs, and communication networks, emerge naturally from various real-world situations.
+Analyzing these graphs leads to findings and understanding of the underlying structures, coherences, and dependencies.
+Recently, methods for embedding graph's nodes into lower-dimensional Euclidean spaces, called graph embeddings, have gained traction in multiple areas of data science research \cite{Goyal_2018}.
+
+Due to the rapid growth of the internet and data accumulation, recommender systems are essential for e-business and online business models to survive and strive in the contemporary market \cite{Polatidis2013RecommenderST}.
+Modern recommender systems need to take into account the huge amounts of user data generated at all times in big data systems around the world and improve recommendations instead of failing under the thrust of big data overload.
+
+Utilizing graph embeddings for recommendation tasks, has recently gained research traction \cite{Palumbo2018AnEC, Palumbo2018KnowledgeGE, GradGyenge2017GraphEB, Sathish2019GraphEB}.
+The advantages of graph embeddings include data compression and the Euclidean feature vector format \cite{Godec2018}.
+Given these advantages and provided competitive results, graph embeddings have the possibility of greatly improving upon graph-based use-cases like recommender systems.
+
+Community Embeddings, in addition to embedding a graph's nodes through first- and second-order proximity, also preserve higher-order proximity by embedding clusters present in the graph data.
+The graph and community embedding algorithm ComE aims to preserve first-, second- and higher-order proximity by embedding a graph's nodes and communities \cite{ComE}.
+
+This work specifically examines community embeddings for friend suggestion recommender systems and evaluates recommendations on social network graph data for the use-case of friend suggestions.
+Graph and community embeddings generated with ComE BGMM+VI are used to develop a friend suggestions recommender system based on the shortest distances between nodes in the embedding.
+Recommendations are evaluated by the top-$N$ recommendations hit-rate of test edges.
+A friend suggestions recommender system with a top-10 leave-one-out hit-rate of 43.6\% and run-time optimized 32.9\% is presented.
 
@@
 
-\begin{thebibliography}{00}
-    \bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-    \bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-    \bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-    \bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-    \bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-    \bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-    \bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
+%%% Bibliography
+\printbibliography
 

### 2020-10-11 conference_101719.tex
FS section done ✅

@@
 \documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+
 \usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
+\usepackage{algorithm}
 \usepackage{graphicx}
@@
 \usepackage[style=numeric, backend=bibtex, language=english, maxbibnames=99]{biblatex}
+
+% tikz
+\usepackage{tikz}
+\usetikzlibrary{shapes.geometric, arrows}
+% tikz styles
+\tikzstyle{user} = [circle, thick, draw, minimum size=2.5cm]
+\tikzstyle{item} = [rectangle, thick, draw, minimum width=3cm, minimum height=1.5cm]
+\tikzstyle{arrow} = [->, draw, thick]
+\tikzstyle{bi-arrow} = [<->, draw, thick]
+\tikzstyle{line} = [-, draw, thick]
 
@@
 
-\title{Community Embeddings for Friend Suggestions\\
-    \thanks{Identify applicable funding agency here. If none, delete this.}
-}
+\title{Community Embeddings for Friend Suggestions}
 
@@
 \begin{IEEEkeywords}
-    graph, embedding, community embedding, recommendations, friend suggestions
+    graph, embedding, community embedding, ComE, recommendations, friend suggestions
 \end{IEEEkeywords}
@@
 
-\section{Ease of Use}
+\section{Friend Suggestions}
 
-\subsection{Maintaining the Integrity of the Specifications}
+Recommender Systems are eagerly researched in academia and widely deployed in real-world business applications.
+Most contemporary technology companies heavily rely on recommender systems to drive usage of their services and consumption of their content.
+Users, in turn, rely on recommender systems to find what they want and need and save searching time.
+State-of-the-art recommender systems provide a competitive advantage desperately needed by online services.
+Companies heavily relying on recommender systems include YouTube, Amazon, Netflix, and many more \cite{Rocca19}.
 
-The IEEEtran class file is used to format your paper and style the text. All margins,
-column widths, line spaces, and text fonts are prescribed; please do not
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement
-and others are deliberate, using specifications that anticipate your paper
-as one part of the entire proceedings, and not as an independent document.
-Please do not revise any of the current designations.
+Recommender systems are built on top of user-item interaction.
+Friend suggestions are a simpler type of recommender system.
+For friend suggestions, no distinction is made between users and items.
+The entity user is both the subject and object of recommendation.
+This results in a simple data model, which can be used for structural friend suggestions, as shown in Fig.
+\ref{fig:data_model}:
+
+\begin{figure}[H]
+    \centering
+    \begin{tikzpicture}[node distance=6cm]
+        \node (user) [user] {User};
+        \path [arrow] (user) edge[loop right] node[right]{relate} (user);
+    \end{tikzpicture}
+    \caption{Minimal data model supporting friend suggestions.}
+    \label{fig:data_model}
+\end{figure}
+
+The two main methods used for recommender systems are collaborative filtering and content-based filtering.
+Collaborative filtering is based on the assumption that users like items similar to other items they like and items that are liked by other users with similar tastes \cite{Grover17, Su2009ASO}.
+Content-based filtering considers user and item attributes, instead of solely interactions \cite{Rocca19, Lops2011SurveyCB}.
+
+In this paper, a method of generating friend suggestions based solely on graph data structure, and not on the node or edge attributes, is presented.
+The graph of users and friendships is embedded to a lower-dimensional space with the community embedding algorithm ComE BGMM+VI \cite{ComE, ComE+, ComE_BGMM_GH}.
+The approach can be considered a variant of collaborative filtering with the euclidean distance of user embeddings and user community membership as measures for user similarity.
+The proposed advantage of using such an approach is that community embeddings optimize first-, second-, and higher-order proximity between users in the node embedding.
+
+\subsection{Evaluation}
+
+To determine the effectivity of friend suggestions, the generated friend suggestions must be properly validated.
+In this paper, the top-$N$ approach to evaluating recommender systems with hit-rate as the evaluation metric is chosen.
+
+A user's top-$N$ recommendations is a list of $N$ items to be recommended to a specific user.
+To evaluate recommender systems with the top-$N$ and hit-rate approach, initially, the dataset is split into train and test data.
+For each testing user, one relation is left out, according to the leave-one-out method and the model is trained on the remaining training dataset.
+Once the model is trained, a list of top-$N$ recommendations is generated for each testing user.
+If the item corresponding to the user is in the user's top-$N$ list, a hit is counted, otherwise, a miss is counted.
+The hit-rate is defined as the total number of hits divided by the number of testing users.
+
+Utilizing the top-$N$ approach with hit-rate to evaluate recommender systems is advantageous to evaluating recommender systems by a link prediction approach since the top-$N$ approach is more realistic in comparison to actual recommender system use-cases.
+When you open Netflix, Amazon, YouTube, or Facebook friend suggestions, one or multiple top-$N$ recommendation lists are generated and displayed.
+If you click on an item and buy, watch, or befriend, that is considered a hit, otherwise, a miss.
+
+The hit-rate metric on top-$N$ recommendations provides a realistic option of evaluating recommender systems \cite{Cremonesi2010PerformanceOR, Palumbo2017entity2rec, Zhao2019ATS}.
 

### 2020-10-11 conference_101719.tex
write intro on alg

@@
 
-\section{Prepare Your Paper Before Styling}
+\section{Algorithm}
+
+The proposed algorithm for generating friend suggestions using community embeddings is detailed and evaluated on time complexity.
+The initially quadratic runtime of generating friend suggestions for all users is then reduced by a factor of $K$ by utilizing a node's community membership.
+The two resulting algorithms are presented.
+
 Before you begin to format your paper, first write and save the content as a

### 2020-10-11 conference_101719.tex
remove template stuff

@@
 
-Before you begin to format your paper, first write and save the content as a
-separate text file. Complete all content and organizational editing before
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on
-proofreading, spelling and grammar.
-
-Keep your text and graphic files separate until after the text has been
-formatted and styled. Do not number text heads---{\LaTeX} will do that
-for you.
-
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text,
-even after they have been defined in the abstract. Abbreviations such as
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use
-abbreviations in the title or heads unless they are unavoidable.
-
-\subsection{Units}
-\begin{itemize}
-    \item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-    \item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-    \item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-    \item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
-
-\subsection{Equations}
-Number equations consecutively. To make your
-equations more compact, you may use the solidus (~/~), the exp function, or
-appropriate exponents. Italicize Roman symbols for quantities and variables,
-but not Greek symbols. Use a long dash rather than a hyphen for a minus
-sign. Punctuate equations with commas or periods when they are part of a
-sentence, as in:
-\begin{equation}
-    a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the
-symbols in your equation have been defined before or immediately following
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-    {\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-    {\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-    \item The word ``data'' is plural, not singular.
-    \item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-    \item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-    \item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-    \item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-    \item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-    \item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-    \item Do not confuse ``imply'' and ``infer''.
-    \item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-    \item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-    \item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A
-minimum of one author is required for all conference articles. Author names
-should be listed starting from left to right and then moving down to the
-next line. This is the author sequence that will be used in future citations
-and by indexing services. Names should not be listed in columns nor group by
-affiliation. Please keep your affiliations as succinct as possible (for
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not
-topically subordinate to each other. Examples include Acknowledgments and
-References and, for these, the correct style to use is ``Heading 5''. Use
-``figure caption'' for your Figure captions, and ``table head'' for your
-table title. Run-in heads, such as ``Abstract'', will require you to apply a
-style (in this case, italic) in addition to the style provided by the drop
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For
-example, the paper title is the primary text head because all subsequent
-material relates and elaborates on this one topic. If there are two or more
-sub-topics, the next level head (uppercase Roman numerals) should be used
-and, conversely, if there are not at least two sub-topics, then no subheads
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and
-bottom of columns. Avoid placing them in the middle of columns. Large
-figures and tables may span across both columns. Figure captions should be
-below the figures; table heads should appear above the tables. Insert
-figures and tables after they are cited in the text. Use the abbreviation
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-    \caption{Table Type Styles}
-    \begin{center}
-        \begin{tabular}{|c|c|c|c|}
-            \hline
-            \textbf{Table} & \multicolumn{3}{|c|}{\textbf{Table Column Head}}                                                         \\
-            \cline{2-4}
-            \textbf{Head}  & \textbf{\textit{Table column subhead}}           & \textbf{\textit{Subhead}} & \textbf{\textit{Subhead}} \\
-            \hline
-            copy           & More table copy$^{\mathrm{a}}$                   &                           &                           \\
-            \hline
-            \multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-        \end{tabular}
-        \label{tab1}
-    \end{center}
-\end{table}
-
-\begin{figure}[htbp]
-    \centerline{\includegraphics{fig1.png}}
-    \caption{Example of a figure caption.}
-    \label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words
-rather than symbols or abbreviations when writing Figure axis labels to
-avoid confusing the reader. As an example, write the quantity
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including
-units in the label, present them within parentheses. Do not label axes only
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of
-quantities and units. For example, write ``Temperature (K)'', not
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B.
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at
-the bottom of the column in which it was cited. Do not put footnotes in the
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use
-``et al.''. Papers that have not been published, even if they have been
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers
-that have been accepted for publication should be cited as ``in press'' \cite{b5}.
-Capitalize only the first word in a paper title, except for proper nouns and
-element symbols.
-
-For papers published in translation journals, please give the English
-citation first, followed by the original foreign-language citation \cite{b6}.
-
 %%% Bibliography

### 2020-10-11 conference_101719.tex
paste in alg stuff from MT

@@
 \usepackage{algorithm}
+\usepackage{algpseudocode}
 \usepackage{graphicx}
@@
 
+\begin{algorithm}[H]
+    \caption{Top-$N$ Social Recommendations based on Node Embeddings}
+    \label{alg:friend_sug}
+    \begin{algorithmic}[1]
+        \Require{graph $G = (V, E)$, maximum number of communities K, number of walks $\gamma$, walk length $\ell$, window size $\zeta$, representation size $D$, negative context size $m$, parameters ($\alpha$, $\beta$), number of recommendations $N$.}
+        \Ensure{Top-$N$ recommendations for all nodes $R$.}
+        % run ComE BGMM+VI
+        \State $\Phi, \Phi', \Pi, (\Psi,\Sigma) \leftarrow ComE_{BGMM+VI}(G, K, \gamma, \ell, \zeta, D, m, \alpha, \beta)$ \Comment{Run ComE BGMM+VI.}
+        % find friends
+        \For{$(v, v') \in E$} \Comment{Determine sets of friends for each user.}
+        \State $F_v \leftarrow F_v \cup \{v'\}$
+        \State $F_{v'} \leftarrow F_{v'} \cup \{v\}$
+        \EndFor
+        % for each node
+        \For{$v \in V$}
+        % generate ascending recommendation list for each node
+        \State $R_v \leftarrow SortedDict(size=N)$ \Comment{Init recommendations for node $v$.}
+        \For{$v' \in V \land v' \notin F_v \land v' \neq v$} \Comment{For all non-friends of user $v$.}
+        \State $d \leftarrow \|\phi_v - \phi_{v'}\|$ \Comment{Distance of $v$ and $v'$ embeddings.}
+        \State $R_v[d] \leftarrow v'$ \Comment{Add $v'$ to $v$'s recommendations at distance $d$.}
+        \EndFor
+        % get Top-N recommendations for each node
+        \State $R_v  \leftarrow R_v.values()$ \Comment{Get top-$N$ recommendations for each node.}
+        \EndFor
+    \end{algorithmic}
+\end{algorithm}
+
+Algorithm \ref{alg:friend_sug} describes in pseudocode how recommendations are computed from node embeddings generated by ComE BGMM+VI.
+The terms friend suggestions and social recommendations are used interchangeably.
+
+The referenced function in line 1 $ComE_{BGMM+VI}(G, \gamma, \ell, \zeta, D, m, \alpha, \beta)$ is the ComE BGMM+VI algorithm as described in Section \ref{sec:ComE_BGMM}.
+ComE BGMM+VI is based on the ComE algorithm presented by \citeauthor{ComE} in their paper \citetitle{ComE} as algorithm 1 on page 381 of the publication's in-proceeding.
+The runtime of ComE BGMM+VI is equivalent to the runtime of ComE in it's big-$O$ notation.
+ComE's time complexity is $O(\abs{V}\gamma\ell + \abs{V} + T_1 (T_2\abs{V}K + K + \abs{E} + \abs{V}\gamma\ell + \abs{V}K))$, which is linear in time complexity to the graph size: $O(\abs{V} + \abs{E})$.\cite{ComE} $T_1$ is the number of iterations of ComE's closed loop consisting of node embedding, community detection, and community embedding to run.
+$T_2$ is the number of iterations to run expectation-maximization or variational inference for community detection and embedding.
+
+ComE uses a Gaussian mixture model and expectation-maximization for community embedding, therefore heavily relying on the number of communities $K$ hyperparameter for embedding quality.
+ComE BGMM+VI instead takes a Bayesian approach by utilizing a Bayesian Gaussian Mixture with variational inference for community embeddings.
+variational inference allows dropping unused communities and therefore is less dependent on the number of communities $K$ hyperparameter.
+In their paper \citetitle{ComE+}, \citeauthor{ComE+} present a Bayesian approach to ComE as algorithm 45 of their publication's magazine.
+ComE+'s time complexity is $O(\abs{V}\gamma\ell + \abs{V} + T_1 (T_2\abs{V}K + K + \abs{E} + \abs{V}\gamma\ell + \abs{V}K))$ as well, which is linear in time complexity to the graph size: $O(\abs{V} + \abs{E})$.\cite{ComE+}
+
+The function $ComE_{BGMM+VI}(G, K, \gamma, \ell, \zeta, D, m, \alpha, \beta)$ returns the node embedding $\Phi$, context embedding $\Phi'$, community assignment $\Pi$, and community embedding $(\Psi,\Sigma)$.
+
+Let us consider the full algorithm's time complexity now:
+\begin{enumerate}
+    \item Line 1: The node and community embeddings are generated with ComE BGMM+VI in linear time to the graph size: $O(\abs{V}\gamma\ell + \abs{V} + T_1 (T_2\abs{V}K + K + \abs{E} + \abs{V}\gamma\ell + \abs{V}K)) = O(\abs{V}\abs{E})$.
+    \item Lines 2-5: All friends of each user are determined in $O(E)$.
+    \item Lines 6 through 13 compute a dictionary of the Top-$N$ friend suggestions for each user sorted ascending by distances between the node embeddings. Each node is considered: $O(\abs{V})$.
+          \begin{enumerate}
+              \item Line 7: A SortedDict is initialized in $O(1)$.
+              \item Lines 8-11: Iterating over all non-friends $v'$ of user $v$ is achieved in $O(\abs{V})$.
+The distance in embedding between user $v$ and $v'$ are calculated in line 9 in $O(1)$.
+In line 10, friend suggestions are added to user $v$'s sorted friends suggestions in $O(N)$.
+The number of friends per user $\overline{\abs{F_v}}$ is not considered, because $\overline{\abs{F_v}} \ll \abs{V}$.
+Lines 8-11 are therefore achievable in $O(\abs{V}N)$.
+              \item Line 12: Friend suggestions are returned as lists of top-$N$ users in $O(1)$.
+          \end{enumerate}
+          Lines 6 through 13 are achieved in $O(\abs{V}^2N))$
+\end{enumerate}
+
+According to the analysis in the list above, the total time complexity of Algorithm \ref{alg:friend_sug} is $O(\abs{V}\gamma\ell + \abs{V} + T_1 (T_2\abs{V}K + K + \abs{E} + \abs{V}\gamma\ell + \abs{V}K) + \abs{E} + \abs{V}^2N)$.
+We consider $\gamma$, $\ell$, $T_1$, $T_2$, and $N$ as constant, therefore the resulting time complexity in big-O notation depends on the graph's size $(\abs{V}, \abs{E})$ and the number of communities $K$: $O(K + \abs{V}K + \abs{E} + \abs{V}^2N)$.
+The number of communities $K$ can also be considered as constant, in which case the time complexity is $O(\abs{E} + \abs{V}^2N)$.
+
+\begin{algorithm}[H]
+    \caption{Top-$N$ Social Recommendations based on Node and Community Embeddings}
+    \label{alg:friend_sug_com}
+    \begin{algorithmic}[1]
+        \Require{graph $G = (V, E)$, maximum number of communities K, number of walks $\gamma$, walk length $\ell$, window size $\zeta$, representation size $D$, negative context size $m$, parameters ($\alpha$, $\beta$), number of recommendations $N$.}
+        \Ensure{Top-$N$ recommendations for all nodes $R$.}
+        % run ComE BGMM+VI
+        \State $\Phi, \Phi', \Pi, (\Psi,\Sigma) \leftarrow ComE_{BGMM+VI}(G, K, \gamma, \ell, \zeta, D, m, \alpha, \beta)$ \Comment{Run ComE BGMM+VI.}
+        %  generate a set of nodes for each community
+        \For{$v \in V$} \Comment{Generate nodes sets $C_k$ per community $k$.}
+        \State $k \leftarrow \pi_v$
+        \State $C_k \leftarrow C_k \cup \{v\}$
+        \EndFor
+        % find friends
+        \For{$(v, v') \in E$} \Comment{Determine sets of friends for each user.}
+        \State $F_v \leftarrow F_v \cup \{v'\}$
+        \State $F_{v'} \leftarrow F_{v'} \cup \{v\}$
+        \EndFor
+        % for each node
+        \For{$v \in V$}
+        % generate ascending recommendation list for each node
+        \State $R_v \leftarrow SortedDict(size=N)$ \Comment{Init recommendations for node $v$.}
+        \For{$v' \in C_k \land v' \notin F_v \land v' \neq v$} \Comment{For all non-friends of user $v$.}
+        \State $d \leftarrow \|\phi_v - \phi_{v'}\|$ \Comment{Distance of $v$ and $v'$ embeddings.}
+        \State $R_v[d] \leftarrow v'$ \Comment{Add $v'$ to $v$'s recommendations at distance $d$.}
+        \EndFor
+        % get Top-N recommendations for each node
+        \State $R_v  \leftarrow R_v.values()$ \Comment{Get top-$N$ recommendations for each node.}
+        \EndFor
+    \end{algorithmic}
+\end{algorithm}
+
+Algorithm \ref{alg:friend_sug_com} describes in pseudocode how recommendations are computed from ComE BGMM+VI node and community embeddings and community assignments.
+The advantage of the second variant of the algorithm, which also considers communities, is that an improvement in time complexity can be obtained, by considering only users in the same community for friend suggestions.
+
+Line 1, lines 6-9, and lines 10-17, except for a small edit in line 12, are the same as in Algorithm \ref{alg:friend_sug}. Differences to Algorithm \ref{alg:friend_sug}:
+
+\begin{enumerate}
+    \item Lines 2-5: All users are filtered into sets $C_k$, one for each community $k$ in $O(\abs{V})$.
+    \item Line 12: Instead of considering the set of all non-friends users of size $\abs{V}$, only users in the same community $C_k$ of size $\frac{\abs{V}}{K}$ are considered.
+Lines 10 through 17 are achievable in $O(\frac{\abs{V}^2N}{K})$.
+\end{enumerate}
+
+According to the analysis from Algorithm \ref{alg:friend_sug} and the differences to Algorithm \ref{alg:friend_sug_com} above, the total time complexity of Algorithm \ref{alg:friend_sug_com} is updated to $O(\abs{V}\gamma\ell + \abs{V} + T_1 (T_2\abs{V}K + K + \abs{E} + \abs{V}\gamma\ell + \abs{V}K) + \abs{V} + \abs{E} + \frac{\abs{V}^2N}{K})$.
+Again, we consider $\gamma$, $\ell$, $T_1$, $T_2$, and $N$ as constant, therefore the resulting time complexity in big-O notation depends on the graph's size $(\abs{V}, \abs{E})$ and the number of communities $K$: $O(K + \abs{V}K + \abs{E} + \frac{\abs{V}^2N}{K})$.
+The number of communities $K$ can also be considered as constant, in which case the time complexity is $O(\abs{E} + \abs{V}^2N)$.
+
+The time complexity of Algorithm \ref{alg:friend_sug_com}, when not considering $K$ as a substantial factor in time complexity is equivalent to the time complexity of Algorithm \ref{alg:friend_sug}.
+Nevertheless, it is clear, that $K$ can substantially reduce the quadratic summand $\abs{V}^2N$ through division by only considering users of the same community for friend suggestions.
+
 %%% Bibliography

### 2020-10-12 conference_101719.tex
do alg section

--- 2020-10-11 conference_101719.tex
@@
 \usepackage{algorithm}
+\usepackage{algpseudocode}
 \usepackage{graphicx}
 \usepackage{textcomp}
+\usepackage{mathtools}
+\usepackage{commath}
 \usepackage[style=numeric, backend=bibtex, language=english, maxbibnames=99]{biblatex}
@@
 
+Algorithm \ref{alg:friend_sug} describes in pseudocode how recommendations are computed from node embeddings generated by ComE BGMM+VI.
+The terms friend suggestions and social recommendations are used interchangeably.
+
+\begin{algorithm}
+    \caption{Top-$N$ Social Recommendations based on Node Embeddings}
+    \label{alg:friend_sug}
+    \begin{algorithmic}[1]
+        \Require{graph $G = (V, E)$, maximum number of communities K, number of walks $\gamma$, walk length $\ell$, window size $\zeta$, representation size $D$, negative context size $m$, parameters ($\alpha$, $\beta$), number of recommendations $N$.}
+        \Ensure{Top-$N$ recommendations for all nodes $R$.}
+        % run ComE BGMM+VI
+        \State $\Phi, \Phi', \Pi, (\Psi,\Sigma) \leftarrow ComE_{BGMM+VI}(G, K, \gamma, \ell, \zeta, D, m, \alpha, \beta)$
+        % find friends
+        \For{$(v, v') \in E$}
+        \State $F_v \leftarrow F_v \cup \{v'\}$
+        \State $F_{v'} \leftarrow F_{v'} \cup \{v\}$
+        \EndFor
+        % for each node
+        \For{$v \in V$}
+        % generate ascending recommendation list for each node
+        \State $R_v \leftarrow SortedDict(size=N)$
+        \For{$v' \in V \land v' \notin F_v \land v' \neq v$}
+        \State $d \leftarrow \|\phi_v - \phi_{v'}\|$
+        \State $R_v[d] \leftarrow v'$
+        \EndFor
+        % get Top-N recommendations for each node
+        \State $R_v  \leftarrow R_v.values()$
+        \EndFor
+    \end{algorithmic}
+\end{algorithm}
+
+The function referenced on line 1, $ComE_{BGMM+VI}(G, \gamma, \ell, \zeta, D, m, \alpha, \beta)$ is the ComE BGMM+VI community embedding algorithm.
+ComE BGMM+VI is based on the ComE algorithm presented by \citeauthor{ComE} in their paper \citetitle{ComE} as algorithm 1 on page 381 of the publication's in-proceeding \cite{ComE}.
+ComE BGMM+VI takes a Bayesian approach to community embedding by utilizing  a Bayesian Gaussian mixture model (BGMM) and variational inference (VI) for community embedding and detection instead of a non-Bayesian Gaussian mixture model (GMM) with expectation maximization (EM) \cite{ComE_BGMM_GH}.
+%TODO citation to the ComE BGMM paper.
+
+The function $ComE_{BGMM+VI}(G, K, \gamma, \ell, \zeta, D, m, \alpha, \beta)$ returns the node embedding $\Phi$, context embedding $\Phi'$, community assignment $\Pi$, and community embedding $(\Psi,\Sigma)$.
+
+The runtime of ComE BGMM+VI is equivalent to the runtime of ComE in its big-$O$ notation.
+ComE's time complexity is $O(\abs{V}\gamma\ell + \abs{V} + T_1 (T_2\abs{V}K + K + \abs{E} + \abs{V}\gamma\ell + \abs{V}K))$, which is linear in time complexity to the graph size: $O(\abs{V} + \abs{E})$ \cite{ComE}.
+
+The node and community embeddings are generated with ComE BGMM+VI in linear time to the graph size: $O(\abs{V}\abs{E})$ (line 1).
+All friends of each user are determined in $O(E)$ (lines 2-5).
+A sorted dictionary of the top-$N$ friend suggestions for each user sorted ascending by distances between the node embeddings is computed in $O(\abs{V}^2N))$ (lines 6-13).
+Top-$N$ friend suggestions are generated for each user ($O(\abs{V})$).
+For each user, all users not befriended currently are considered ($O(\abs{V})$) and inserted into a sorted dictionary of length $N$ ($O(N)$).
+
+This brings the total time complexity of Algorithm \ref{alg:friend_sug} to $O(\abs{V}\gamma\ell + \abs{V} + T_1 (T_2\abs{V}K + K + \abs{E} + \abs{V}\gamma\ell + \abs{V}K) + \abs{E} + \abs{V}^2N)$.
+We consider $\gamma$, $\ell$, $T_1$, $T_2$, and $N$ as constant w.r.t the data, therefore the resulting time complexity in big-O notation depends on the graph's size $(\abs{V}, \abs{E})$ and the number of communities $K$: $O(K + \abs{V}K + \abs{E} + \abs{V}^2N)$.
+The number of communities $K$ can also be considered as constant, in which case the time complexity is $O(\abs{E} + \abs{V}^2N)$.
+
+Algorithm \ref{alg:friend_sug_com} describes in pseudocode how recommendations are computed from ComE BGMM+VI node and community embeddings and community assignments.
+The advantage of also considers community membership, is that an improvement in time complexity can be obtained, by considering only users in the same community for friend suggestions.
+
+\begin{algorithm}
+    \caption{Top-$N$ Social Recommendations based on Node and Community Embeddings}
+    \label{alg:friend_sug_com}
+    \begin{algorithmic}[1]
+        \Require{graph $G = (V, E)$, maximum number of communities K, number of walks $\gamma$, walk length $\ell$, window size $\zeta$, representation size $D$, negative context size $m$, parameters ($\alpha$, $\beta$), number of recommendations $N$.}
+        \Ensure{Top-$N$ recommendations for all nodes $R$.}
+        % run ComE BGMM+VI
+        \State $\Phi, \Phi', \Pi, (\Psi,\Sigma) \leftarrow ComE_{BGMM+VI}(G, K, \gamma, \ell, \zeta, D, m, \alpha, \beta)$ \Comment{Run ComE BGMM+VI.}
+        %  generate a set of nodes for each community
+        \For{$v \in V$} \Comment{Generate nodes sets $C_k$ per community $k$.}
+        \State $k \leftarrow \pi_v$
+        \State $C_k \leftarrow C_k \cup \{v\}$
+        \EndFor
+        % find friends
+        \For{$(v, v') \in E$} \Comment{Determine sets of friends for each user.}
+        \State $F_v \leftarrow F_v \cup \{v'\}$
+        \State $F_{v'} \leftarrow F_{v'} \cup \{v\}$
+        \EndFor
+        % for each node
+        \For{$v \in V$}
+        % generate ascending recommendation list for each node
+        \State $R_v \leftarrow SortedDict(size=N)$ \Comment{Init recommendations for node $v$.}
+        \For{$v' \in C_k \land v' \notin F_v \land v' \neq v$} \Comment{For all non-friends of user $v$.}
+        \State $d \leftarrow \|\phi_v - \phi_{v'}\|$ \Comment{Distance of $v$ and $v'$ embeddings.}
+        \State $R_v[d] \leftarrow v'$ \Comment{Add $v'$ to $v$'s recommendations at distance $d$.}
+        \EndFor
+        % get Top-N recommendations for each node
+        \State $R_v  \leftarrow R_v.values()$ \Comment{Get top-$N$ recommendations for each node.}
+        \EndFor
+    \end{algorithmic}
+\end{algorithm}
+
+Line 1, lines 6-9, and lines 10-17, except for line 12, are the same in Algorithm \ref{alg:friend_sug_com} as in Algorithm \ref{alg:friend_sug}.
+All users are filtered into sets $C_k$, one for each community $k$ in $O(\abs{V})$ (lines 2-5).
+Instead of considering the set of all non-friends users of size $\abs{V}$, only users in the same community $C_k$ of size $\frac{\abs{V}}{K}$ are considered (line 12) in $O(\frac{\abs{V}^2N}{K})$.
+
+This brings the total time complexity of Algorithm \ref{alg:friend_sug_com} to $O(\abs{V}\gamma\ell + \abs{V} + T_1 (T_2\abs{V}K + K + \abs{E} + \abs{V}\gamma\ell + \abs{V}K) + \abs{V} + \abs{E} + \frac{\abs{V}^2N}{K})$.
+Again, we consider $\gamma$, $\ell$, $T_1$, $T_2$, and $N$ as constant, therefore the resulting time complexity in big-O notation depends on the graph's size $(\abs{V}, \abs{E})$ and the number of communities $K$: $O(K + \abs{V}K + \abs{E} + \frac{\abs{V}^2N}{K})$.
+The number of communities $K$ can also be considered as constant, in which case the time complexity is $O(\abs{E} + \abs{V}^2N)$.
+
+The time complexity of Algorithm \ref{alg:friend_sug_com}, when not considering $K$ as a substantial factor in time complexity is equivalent to the time complexity of Algorithm \ref{alg:friend_sug}.
+Nevertheless, $K$ can substantially reduce the quadratic summand $\abs{V}^2N$ through division by only considering users of the same community for friend suggestions.
+The reduction in time complexity through Algorithm \ref{alg:friend_sug_com} is only scalable when considering $K$ to be variable with the input dataset's graph size.
+This assumption can be made when considering communities as broad groups of friends for friend suggestions.
+With ten times more users, these users form ten times more communities.
+
 %%% Bibliography

### 2020-10-12 conference_101719.tex
remove comments from pseudocode alg
do alg done

@@
         % run ComE BGMM+VI
-        \State $\Phi, \Phi', \Pi, (\Psi,\Sigma) \leftarrow ComE_{BGMM+VI}(G, K, \gamma, \ell, \zeta, D, m, \alpha, \beta)$
+        \State $\Phi, \Phi', \Pi, (\Psi,\Sigma) \leftarrow ComE(G, K, \gamma, \ell, \zeta, D, m, \alpha, \beta)$
         % find friends
@@
 
-The function referenced on line 1, $ComE_{BGMM+VI}(G, \gamma, \ell, \zeta, D, m, \alpha, \beta)$ is the ComE BGMM+VI community embedding algorithm.
+The function $ComE(G, K, \gamma, \ell, \zeta, D, m, \alpha, \beta)$ is the ComE BGMM+VI community embedding algorithm.
+It returns the node embedding $\Phi$, context embedding $\Phi'$, community assignment $\Pi$, and community embedding $(\Psi,\Sigma)$.
 ComE BGMM+VI is based on the ComE algorithm presented by \citeauthor{ComE} in their paper \citetitle{ComE} as algorithm 1 on page 381 of the publication's in-proceeding \cite{ComE}.
@@
 
-The function $ComE_{BGMM+VI}(G, K, \gamma, \ell, \zeta, D, m, \alpha, \beta)$ returns the node embedding $\Phi$, context embedding $\Phi'$, community assignment $\Pi$, and community embedding $(\Psi,\Sigma)$.
-
 The runtime of ComE BGMM+VI is equivalent to the runtime of ComE in its big-$O$ notation.
-ComE's time complexity is $O(\abs{V}\gamma\ell + \abs{V} + T_1 (T_2\abs{V}K + K + \abs{E} + \abs{V}\gamma\ell + \abs{V}K))$, which is linear in time complexity to the graph size: $O(\abs{V} + \abs{E})$ \cite{ComE}.
-
-The node and community embeddings are generated with ComE BGMM+VI in linear time to the graph size: $O(\abs{V}\abs{E})$ (line 1).
+ComE's time complexity is $O(\abs{V}\gamma\ell + \abs{V} + T_1 (T_2\abs{V}K + K + \abs{E} + \abs{V}\gamma\ell + \abs{V}K))$, which is linear in time complexity to the graph size: $O(\abs{V} + \abs{E})$ (line 1) \cite{ComE}.
 All friends of each user are determined in $O(E)$ (lines 2-5).
 A sorted dictionary of the top-$N$ friend suggestions for each user sorted ascending by distances between the node embeddings is computed in $O(\abs{V}^2N))$ (lines 6-13).
-Top-$N$ friend suggestions are generated for each user ($O(\abs{V})$).
+Top-$N$ friend suggestions are generated for each user: $O(\abs{V})$.
 For each user, all users not befriended currently are considered ($O(\abs{V})$) and inserted into a sorted dictionary of length $N$ ($O(N)$).
@@
 This brings the total time complexity of Algorithm \ref{alg:friend_sug} to $O(\abs{V}\gamma\ell + \abs{V} + T_1 (T_2\abs{V}K + K + \abs{E} + \abs{V}\gamma\ell + \abs{V}K) + \abs{E} + \abs{V}^2N)$.
-We consider $\gamma$, $\ell$, $T_1$, $T_2$, and $N$ as constant w.r.t the data, therefore the resulting time complexity in big-O notation depends on the graph's size $(\abs{V}, \abs{E})$ and the number of communities $K$: $O(K + \abs{V}K + \abs{E} + \abs{V}^2N)$.
-The number of communities $K$ can also be considered as constant, in which case the time complexity is $O(\abs{E} + \abs{V}^2N)$.
+We consider $\gamma$, $\ell$, $T_1$, $T_2$, and $N$ as constant, therefore the time complexity depends on the graph's size $(\abs{V}, \abs{E})$ and the number of communities $K$: $O(K + \abs{V}K + \abs{E} + \abs{V}^2)$.
 
@@
         % run ComE BGMM+VI
-        \State $\Phi, \Phi', \Pi, (\Psi,\Sigma) \leftarrow ComE_{BGMM+VI}(G, K, \gamma, \ell, \zeta, D, m, \alpha, \beta)$ \Comment{Run ComE BGMM+VI.}
+        \State $\Phi, \Phi', \Pi, (\Psi,\Sigma) \leftarrow ComE(G, K, \gamma, \ell, \zeta, D, m, \alpha, \beta)$
         %  generate a set of nodes for each community
-        \For{$v \in V$} \Comment{Generate nodes sets $C_k$ per community $k$.}
+        \For{$v \in V$}
         \State $k \leftarrow \pi_v$
@@
         % find friends
-        \For{$(v, v') \in E$} \Comment{Determine sets of friends for each user.}
+        \For{$(v, v') \in E$}
         \State $F_v \leftarrow F_v \cup \{v'\}$
@@
         % generate ascending recommendation list for each node
-        \State $R_v \leftarrow SortedDict(size=N)$ \Comment{Init recommendations for node $v$.}
-        \For{$v' \in C_k \land v' \notin F_v \land v' \neq v$} \Comment{For all non-friends of user $v$.}
-        \State $d \leftarrow \|\phi_v - \phi_{v'}\|$ \Comment{Distance of $v$ and $v'$ embeddings.}
-        \State $R_v[d] \leftarrow v'$ \Comment{Add $v'$ to $v$'s recommendations at distance $d$.}
+        \State $R_v \leftarrow SortedDict(size=N)$
+        \For{$v' \in C_k \land v' \notin F_v \land v' \neq v$}
+        \State $d \leftarrow \|\phi_v - \phi_{v'}\|$
+        \State $R_v[d] \leftarrow v'$
         \EndFor
         % get Top-N recommendations for each node
-        \State $R_v  \leftarrow R_v.values()$ \Comment{Get top-$N$ recommendations for each node.}
+        \State $R_v  \leftarrow R_v.values()$
         \EndFor
@@
 This brings the total time complexity of Algorithm \ref{alg:friend_sug_com} to $O(\abs{V}\gamma\ell + \abs{V} + T_1 (T_2\abs{V}K + K + \abs{E} + \abs{V}\gamma\ell + \abs{V}K) + \abs{V} + \abs{E} + \frac{\abs{V}^2N}{K})$.
-Again, we consider $\gamma$, $\ell$, $T_1$, $T_2$, and $N$ as constant, therefore the resulting time complexity in big-O notation depends on the graph's size $(\abs{V}, \abs{E})$ and the number of communities $K$: $O(K + \abs{V}K + \abs{E} + \frac{\abs{V}^2N}{K})$.
-The number of communities $K$ can also be considered as constant, in which case the time complexity is $O(\abs{E} + \abs{V}^2N)$.
+Again, we consider $\gamma$, $\ell$, $T_1$, $T_2$, and $N$ as constant, therefore the time complexity depends on the graph's size $(\abs{V}, \abs{E})$ and the number of communities $K$: $O(K + \abs{V}K + \abs{E} + \frac{\abs{V}^2}{K})$.
 
-The time complexity of Algorithm \ref{alg:friend_sug_com}, when not considering $K$ as a substantial factor in time complexity is equivalent to the time complexity of Algorithm \ref{alg:friend_sug}.
-Nevertheless, $K$ can substantially reduce the quadratic summand $\abs{V}^2N$ through division by only considering users of the same community for friend suggestions.
-The reduction in time complexity through Algorithm \ref{alg:friend_sug_com} is only scalable when considering $K$ to be variable with the input dataset's graph size.
-This assumption can be made when considering communities as broad groups of friends for friend suggestions.
-With ten times more users, these users form ten times more communities.
+The hyper-parameter number of communities $K$ can reduce the quadratic summand $\abs{V}^2N$ by only considering users of the same community for friend suggestions.
+The reduction in time complexity through Algorithm \ref{alg:friend_sug_com} is only scalable when considering $K$ to be scale with the input graph's size.
+This assumption can be made when considering communities as groups of friends: with ten times more users, these users form ten times more communities.
 

### 2020-10-12 conference_101719.tex
next: Visual Example
visual example done

@@
 \usepackage{textcomp}
+\usepackage{multirow}
 \usepackage{mathtools}
 \usepackage{commath}
+\usepackage{subcaption}
 \usepackage[style=numeric, backend=bibtex, language=english, maxbibnames=99]{biblatex}
@@
 
-The hyper-parameter number of communities $K$ can reduce the quadratic summand $\abs{V}^2N$ by only considering users of the same community for friend suggestions.
+The runtimes for Algorithm \ref{alg:friend_sug} and \ref{alg:friend_sug_com} when considering $K$ as constant or scaling w.r.t the graph $G = (V, E)$ are shown in Table \ref{tab:runtimes}.
+The number of friend suggestions $N$ is considered constant w.r.t the graph $G = (V, E)$.
+
+\begin{table}
+    \centering
+    \caption{Algorithm \ref{alg:friend_sug} and \ref{alg:friend_sug_com} time complexity.}
+    \label{tab:runtimes}
+    \begin{tabular}{l l | c}
+        \multirow{2}{*}{$K$ constant} & Algorithm \ref{alg:friend_sug}     & $O(\abs{E} + \abs{V}^2)$                          \\
+                                      & Algorithm \ref{alg:friend_sug_com} & $O(\abs{E} + \abs{V}^2)$                          \\
+        \hline
+        \multirow{2}{*}{$K$ scaling}  & Algorithm \ref{alg:friend_sug}     & $O(K + \abs{V}K + \abs{E} + \abs{V}^2)$           \\
+                                      & Algorithm \ref{alg:friend_sug_com} & $O(K + \abs{V}K + \abs{E} + \frac{\abs{V}^2}{K})$ \\
+    \end{tabular}
+\end{table}
+
+When the hyperparameter number of communities $K$ is considered non-constant with respect to the graph $G$, Algorithm \ref{alg:friend_sug_com} reduces the quadratic runtime in comparison to Algorithm \ref{alg:friend_sug_com}.
+$K$ can therefore reduce the quadratic summand $\abs{V}^2N$ by only considering users of the same community for friend suggestions.
 The reduction in time complexity through Algorithm \ref{alg:friend_sug_com} is only scalable when considering $K$ to be scale with the input graph's size.
 This assumption can be made when considering communities as groups of friends: with ten times more users, these users form ten times more communities.
+
+\section{Visual Example}
+
+The small \citetitle{KarateClubDS} dataset will be used to visually underline the motivation for using node embedding and community memberships generated by ComE BGMM+VI for generating friend suggestions for person nodes on the karate club graph \cite{KarateClubDS}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.4\textwidth]{images/karateclub/spring.png}
+    \caption{\citetitle{KarateClubDS} plotted with networkx's spring layout \cite{KarateClubDS, networkx}.}
+    \label{fig:karateclub_spring}
+\end{figure}
+
+Fig.
+\ref{fig:karateclub_spring} shows the 34 nodes and 78 edges of the \citetitle{KarateClubDS} dataset plotted as a graph with the Python network package networkx's spring layout.\cite{networkx} Spring layout simulates a force-directed representation of the network, by treating edges as springs pulling nodes together and treating nodes as repelling objects, sometimes called an anti-gravity force.\cite{networkx} The node classification, represented by node color, shown in Fig.
+\ref{fig:karateclub_spring} was obtained by running ComE with BGMM and VI with the hyperparameters presented in Table \ref{tab:params_karateclub}.
+
+\begin{table}
+    \centering
+    \caption{Hyperparameters used for the Karateclub dataset.}
+    \label{tab:params_karateclub}
+    \begin{tabular}{ l | c | r }
+        parameter                    & notation & value     \\
+        \hline
+        \hline
+        number\_walks                & $\gamma$ & $10$      \\
+        \hline
+        walk\_length                 & $\ell$   & $80$      \\
+        \hline
+        representation\_size         & $D$      & $2$       \\
+        \hline
+        num\_workers                 & \empty   & $10$      \\
+        \hline
+        num\_iter                    & \empty   & $3$       \\
+        \hline
+        reg\_covar                   & \empty   & $0.00001$ \\
+        \hline
+        batch\_size                  & \empty   & $50$      \\
+        \hline
+        window\_size                 & $\zeta$  & $10$      \\
+        \hline
+        negative                     & $m$      & $5$       \\
+        \hline
+        lr                           & \empty   & $0.025$   \\
+        \hline
+        alpha                        & $\alpha$ & $0.1$     \\
+        \hline
+        beta                         & $\beta$  & $0.1$     \\
+        \hline
+        down\_sampling               & \empty   & $0.0$     \\
+        \hline
+        communities                  & $K$      & $5$       \\
+        \hline
+        weight\_concentration\_prior & $\Gamma$ & $10^{-5}$ \\
+    \end{tabular}
+\end{table}
+
+As can be seen in Figure \ref{fig:karateclub_spring}, the two communities in the \citetitle{KarateClubDS} dataset are correctly identified, despite the number of communities being initialized with $K=5$.
+Thanks to the Bayesian approach to community modeling and optimization through variational inference, three unused communities are dropped, which leaves the prominent two communities present in the dataset.
+The node classification obtained reflects the node classification published in the \citeyear{ComE} original ComE paper by \citeauthor{ComE}.\cite{ComE}
+
+\subsection{Training and Testing Split}
+
+\citetitle{KarateClubDS} is split into training and testing parts.
+For evaluation, the leave-one-out (LOO) method is used, where for each testing user one edge is left out, then if the left out edge is in the user's top-$N$ recommendations, a hit is counted, otherwise, a miss is recorded.
+The leave-one-out method is used in literature for evaluating recommender systems.\cite{Zhao2019ATS, He2017NeuralCF}
+
+The three users with the highest degree are chosen as testing users: user 30, user 0, and user 32.
+For each testing user, a LOO-testing edge is chosen: (30, 23), (0, 1), and (32, 30).
+These three edges are spared for the testing dataset and omitted from the training graph,
+
+\subsection{Embedding}
+
+ComE BGMM+VI is run with the hyperparameters listed in Table \ref{tab:params_karateclub} on the training dataset.
+The resulting node and community embeddings are visualized as node embeddings colored by community membership and community embeddings plotted as ellipses in Fig.
+\ref{fig:karateclub_emb}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=1\linewidth]{images/karateclub/embeddings_5.png}
+    \caption{\citetitle{KarateClubDS} training dataset node and community embedding and node classification.}
+    \label{fig:karateclub_emb}
+\end{figure}
+
+\subsection{Friend Suggesting}
+
+With embeddings generated, top-$N$ friend suggestion recommendations are generated from the training node and community embeddings for the testing users.
+For each testing user, a ranked list of non-friend users from the same community is generated (Algorithm \ref{alg:friend_sug_com}).
+A test user's friend suggestion list is ordered in ascending order by the euclidean distance between the node embeddings.
+Table \ref{tab:karateclub_emb_dists} shows the test users' friend suggestion ranked lists.
+
+\begin{table}
+    \centering
+    \caption{Testing users' friend suggestions ranked by node embedding distance.}
+    \label{tab:karateclub_emb_dists}
+    \begin{subfigure}{.4\textwidth}
+        \centering
+        \begin{tabular}{ c | r }
+            User        & Distance   \\
+            \hline
+            \hline
+            24          & $0.137181$ \\
+            \hline
+            25          & $0.214332$ \\
+            \hline
+            \textbf{23} & $0.543287$ \\
+        \end{tabular}
+        \caption{user 33}
+    \end{subfigure}
+    \begin{subfigure}{.4\textwidth}
+        \centering
+        \begin{tabular}{ c | r }
+            User       & Distance   \\
+            \hline
+            \hline
+            \textbf{1} & $0.322270$ \\
+            \hline
+            16         & $1.030336$ \\
+        \end{tabular}
+        \caption{user 0}
+    \end{subfigure}
+    \begin{subfigure}{.4\textwidth}
+        \centering
+        \begin{tabular}{ c | r }
+            User        & Distance   \\
+            \hline
+            \hline
+            25          & $0.039816$ \\
+            \hline
+            24          & $0.045994$ \\
+            \hline
+            27          & $0.182484$ \\
+            \hline
+            26          & $0.255288$ \\
+            \hline
+            28          & $0.356683$ \\
+            \hline
+            9           & $0.501317$ \\
+            \hline
+            \textbf{30} & $0.668306$ \\
+        \end{tabular}
+        \caption{user 32}
+    \end{subfigure}
+\end{table}
+
+The testing users' removed edges make it to the lists successfully; therefore, the removed friends are in the same community as the test users and can be recommended through friend suggestions.
+
+\subsection{Evaluation}
+
+The top-$N$ friend suggestions, generated for the testing users with Algorithm \ref{alg:friend_sug_com}, are evaluated against the three removed test edges.
+The ranked lists of friend-suggestions shown in Figure \ref{tab:karateclub_emb_dists} is used to determine top-$N$ friend suggestions for each testing user and evaluate the recommendations my the hit-rate metric.
+The LOO-testing edges are printed bold in Table \ref{tab:karateclub_emb_dists}.
+The resulting top-$N$ hit-rates are plotted against the number of suggestions $N$ in Fig.
+\ref{fig:karateclub_hitrates}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.4\textwidth]{images/karateclub/hit_rates.png}
+    \caption{Hit-rates from top-$N$ recommendations on \citetitle{KarateClubDS}.}
+    \label{fig:karateclub_hitrates}
+\end{figure}
+
+Fig.
+\ref{fig:karateclub_hitrates} shows promising results for using ComE to generate top-$N$ friend suggestions on the small \citetitle{KarateClubDS}.
+The achieved hit-rate starts at 33\% for $N=1$, reaches 67\% at $N=3$, and maxes out at 100\% for $N=7$; therefore, when presenting three friend suggestions to one test user, at least in $66\%$ of cases a friend suggestion would be of interest.
 

### 2020-10-12 conference_101719.tex
next: Facebook Friend Suggestions
FFS intro

@@
 
+\section{Facebook Friend Suggestions}
+
+The recommender system based on community embeddings with the Bayesian Gaussian mixture model and variational inference is quantitatively evaluated.
+Friend suggestions are generated for the \citetitle{social_circles_fb} dataset \cite{social_circles_fb, social_circles_in_ego_networks}.
+
+The method of generating friend suggestions using ComE BGMM+VI embeddings and the smallest-distance approach is applied to the \citetitle{social_circles_fb} graph.
+Both Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} are evaluated.
+The top-$N$ recommendations are evaluated by the hit-rate metric.
+
 %%% Bibliography

### 2020-10-12 conference_101719.tex
add figure to p1
structure
extend citation

@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=0.48\textwidth]{images/fb/graph_d4.png}
+    \caption{\citetitle{social_circles_fb} graph plotted with networkx's spring layout and node colors representing community membership obtained by ComE BGMM+VI with $D=4$.\cite{networkx}}
+    \label{fig:fb_graph}
+\end{figure}
+
 \section{Friend Suggestions}
@@
 This results in a simple data model, which can be used for structural friend suggestions, as shown in Fig.
-\ref{fig:data_model}:
+\ref{fig:data_model}.
 
-\begin{figure}[H]
+\begin{figure}[h]
     \centering
@@
 
-The hit-rate metric on top-$N$ recommendations provides a realistic option of evaluating recommender systems \cite{Cremonesi2010PerformanceOR, Palumbo2017entity2rec, Zhao2019ATS}.
+The hit-rate metric on top-$N$ recommendations provides a realistic option of evaluating recommender systems and with the leave-one-out (LOO) strategy is used often in literature \cite{Cremonesi2010PerformanceOR, Palumbo2017entity2rec, Zhao2019ATS, He2017NeuralCF}.
 

### 2020-10-12 conference_101719.tex
remove and add some

@@
 For evaluation, the leave-one-out (LOO) method is used, where for each testing user one edge is left out, then if the left out edge is in the user's top-$N$ recommendations, a hit is counted, otherwise, a miss is recorded.
-The leave-one-out method is used in literature for evaluating recommender systems.\cite{Zhao2019ATS, He2017NeuralCF}
 
@@
 For each testing user, a LOO-testing edge is chosen: (30, 23), (0, 1), and (32, 30).
-These three edges are spared for the testing dataset and omitted from the training graph,
+These three testing edges are spared for the testing dataset and omitted from the training graph.
 

### 2020-10-12 conference_101719.tex
write FFS dataset and train-test split

@@
 
+\subsection{Dataset}
+
+The \citetitle{social_circles_fb} dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \citetitle{social_circles_in_ego_networks}.\cite{social_circles_in_ego_networks}
+
+Fig.
+\ref{fig:egonet} shows an illustration of the ego-network of user $u$.
+User $u$ has direct connections to $v_i$, called alters.
+Alters can be connected to each other and build circles of users, like families, high school friends, or college friends.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.48\textwidth]{images/fb/egonet.png}
+    \caption{Illustrative example of an ego-network \cite{social_circles_in_ego_networks}.}
+    \label{fig:egonet}
+\end{figure}
+
+\citeauthor{social_circles_in_ego_networks} obtained profile and network data from ten Facebook ego-networks. The dataset contains 4039 users (nodes) and 88234 friendships (edges).
+
+\subsection{Training and Testing Split}
+
+The \citetitle{social_circles_fb} graph is split into training and testing parts.
+For evaluation, the leave-one-out (LOO) method is used, where for each testing user one edge is left out, then if the left out edge is in the user's top-$N$ recommendations, a hit is counted, otherwise, a miss is recorded.
+Users with only one connection are removed from the dataset since no network information is added by them.
+
+$1169$ of the 4039 users of the \citetitle{social_circles_fb} graph have at least $50$ connections and are used for testing friend suggestions.
+The threshold of $50$ friends for considering users for testing is set to make sure enough data is available to make sensable suggestions for testing users.
+
+Now that the testing users are identified, the leave-one-out method is employed for obtaining one testing friendship per testing user.
+The friendship chosen to leave out for testing for each testing user is chosen randomly using NumPy's random choice.\cite{oliphant2006guide, van2011numpy}
+
 %%% Bibliography

### 2020-10-12 conference_101719.tex
write some embedding FFS
add embedding stuff from MT

@@
 \usepackage{algpseudocode}
+\usepackage{xcolor}
 \usepackage{graphicx}
@@
 \usepackage{subcaption}
+\usepackage[super]{nth}
 \usepackage[style=numeric, backend=bibtex, language=english, maxbibnames=99]{biblatex}
@@
 
+\subsection{Embedding}
+
+Community embeddings for the \citetitle{social_circles_fb} graph are generated by running ComE BGMM+VI with the hyperparameters listed in Table \ref{tab:params_fb}.
+
+\begin{table}
+    \centering
+    \caption{Hyperparameters used for the \citetitle{social_circles_fb} dataset.}
+    \label{tab:params_fb}
+    \begin{tabular}{ l | c | r }
+        parameter                    & notation & value       \\
+        \hline
+        \hline
+        number\_walks                & $\gamma$ & $10$        \\
+        \hline
+        walk\_length                 & $\ell$   & $80$        \\
+        \hline
+        representation\_size         & $D$      & $2, 4, 128$ \\
+        \hline
+        num\_workers                 & \empty   & $10$        \\
+        \hline
+        num\_iter                    & \empty   & $3$         \\
+        \hline
+        com\_n\_init                 & \empty   & $10$        \\
+        \hline
+        reg\_covar                   & \empty   & $0.00001$   \\
+        \hline
+        batch\_size                  & \empty   & $50$        \\
+        \hline
+        window\_size                 & $\zeta$  & $10$        \\
+        \hline
+        negative                     & $m$      & $5$         \\
+        \hline
+        lr                           & \empty   & $0.025$     \\
+        \hline
+        alpha                        & $\alpha$ & $0.1$       \\
+        \hline
+        beta                         & $\beta$  & $0.1$       \\
+        \hline
+        down\_sampling               & \empty   & $0.0$       \\
+        \hline
+        communities                  & $K$      & $10$        \\
+        \hline
+        weight\_concentration\_prior & $\Gamma$ & $10^{-5}$   \\
+    \end{tabular}
+\end{table}
+
+As is shown in Table \ref{tab:params_fb}, the embedding's representation size $D$ is varied along three values.
+A representation size $D \in [2,4,128]$ is chosen to determine the effect of the embedding's dimensionality on friend suggestions.
+It is hypothesized, that two dimensions are not sufficient to capture the structure of the \citetitle{social_circles_fb} graph, due to its size, therefore higher dimensional embeddings are evaluated as well.
+
+Fig.
+\ref{fig:fb_emb_anim_d2}, Fig.
+\ref{fig:fb_emb_anim_d4}, and Fig.
+\ref{fig:fb_emb_anim_d128} show the node embeddings generated by ComE BGMM+VI after one, two, and three iterations.
+The nodes are colored by community membership from ComE's community embedding and detection.
+The $4$- and $128$-dimensional node and community embeddings cannot effectively be plotted in two-dimensional print.
+Instead, in Figures \ref{fig:fb_emb_anim_d4} and \ref{fig:fb_emb_anim_d128} the two first dimensions of the node and community embeddings are plotted to gain a narrow perspective on the resulting node embeddings.
+
+\newcommand{\fbEmbAnimD}[1]{
+    \begin{figure*}
+        \centering
+        \begin{subfigure}{.33\textwidth}
+            \centering
+            \includegraphics[width=1\linewidth]{images/fb/anim_d#1_i0.png}
+            \caption{\nth{1} Iteration \\$D=#1$.}
+        \end{subfigure}%
+        %
+        \begin{subfigure}{.33\textwidth}
+            \centering
+            \includegraphics[width=1\linewidth]{images/fb/anim_d#1_i1.png}
+            \caption{\nth{2} Iteration\\$D=#1$}
+        \end{subfigure}%
+        %
+        \begin{subfigure}{.33\textwidth}
+            \centering
+            \includegraphics[width=1\linewidth]{images/fb/anim_d#1_i2.png}
+            \caption{\nth{3} Iteration\\$D=#1$}
+        \end{subfigure}%
+        %
+        \caption{Node embeddings segment with representation size $D=#1$.}
+        \label{fig:fb_emb_anim_d#1}
+    \end{figure*}
+}
+
+\fbEmbAnimD{2}
+\fbEmbAnimD{4}
+\fbEmbAnimD{128}
+
+Fig.
+\ref{fig:fb_graphs} shows the graph spring plotted with networkx and nodes colored by community membership after the lastest iteration of ComE.\cite{networkx} The spring plotted graph structure on Figure \ref{fig:fb_graphs} suggest, that with embedding dimension $D=4$, more fitting communities are detected than for $D=2$ and $D=128$.
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}{.33\textwidth}
+        \centering
+        \includegraphics[width=1\linewidth]{images/fb/graph_d2.png}
+        \caption{$D=2$}
+    \end{subfigure}%
+    %
+    \begin{subfigure}{.33\textwidth}
+        \centering
+        \includegraphics[width=1\linewidth]{images/fb/graph_d4.png}
+        \caption{$D=4$}
+    \end{subfigure}%
+    %
+    \begin{subfigure}{.33\textwidth}
+        \centering
+        \includegraphics[width=1\linewidth]{images/fb/graph_d128.png}
+        \caption{$D=128$}
+    \end{subfigure}%
+    %
+    \caption{Spring plotted graphs with nodes colored by community membership after last ComE BGMM+VI iteration.}
+    \label{fig:fb_graphs}
+\end{figure*}
+
+Figure \ref{fig:fb_emb_anim_d2} shows node and community embeddings with representation size $D=2$.
+The limiting two-dimensional space does not allow ComE to represent the \citetitle{social_circles_fb} graph's structure sufficiently to utilize the $K=10$ components of the Gaussian mixture model.
+Only three components are used after the last of three iterations.
+
+While Figures \ref{fig:fb_emb_anim_d4} and \ref{fig:fb_emb_anim_d128} show only the first two dimensions, of the node embedding of 4 or 128 dimensionality respectively, the general structure of communities is visible.
+The development of the node embeddings over the three iterations shows the manifestation of the first-, second-, and higher-order proximity by ComE's closed loop.
+The node embeddings are densified in their communities and spread out in regards to other communities.
+All $K=10$ components of the Gaussian mixture model are used for $D=4$ and $D=128$.
+
+Node are distributed over the $K=10$ communities as shown in the histogram in Figure \ref{fig:fb_emb_weights}:
+
+\begin{figure*}
+    \centering
+    %
+    \begin{subfigure}{.33\textwidth}
+        \centering
+        \includegraphics[width=1\linewidth]{images/fb/weights_d2.png}
+        \caption{$D=2$}
+        \label{fig:fb_emb_weights_d2}
+    \end{subfigure}%
+    %
+    \begin{subfigure}{.33\textwidth}
+        \centering
+        \includegraphics[width=1\linewidth]{images/fb/weights_d4.png}
+        \caption{$D=4$}
+        \label{fig:fb_emb_weights_d4}
+    \end{subfigure}%
+    %
+    \begin{subfigure}{.33\textwidth}
+        \centering
+        \includegraphics[width=1\linewidth]{images/fb/weights_d128.png}
+        \caption{$D=128$}
+        \label{fig:fb_emb_weights_d128}
+    \end{subfigure}%
+    %
+    \caption{Weights of communities with $K=10$ and $D \in [2,4,128]$.}
+    \label{fig:fb_emb_weights}
+\end{figure*}
+
+Figure \ref{fig:fb_emb_weights_d2} shows that with representation size $D=2$, ComE BGMM+VI drops 6 communites, effecitvelly using only 4 communities in the final embedding, because the two-dimensional node embeddings are not expressive enough to support more communities.
+Figures \ref{fig:fb_emb_weights_d4} and \ref{fig:fb_emb_weights_d128} show that with representation sizes $D=4$ and $D=128$ respectivelly, all $K=10$ communities are used.
+
 %%% Bibliography

### 2020-10-12 conference_101719.tex
compactify
finish  conclusion and FFS

@@
             \includegraphics[width=1\linewidth]{images/fb/anim_d#1_i0.png}
-            \caption{\nth{1} Iteration \\$D=#1$.}
+            \caption{\nth{1} Iteration}
         \end{subfigure}%
@@
             \includegraphics[width=1\linewidth]{images/fb/anim_d#1_i1.png}
-            \caption{\nth{2} Iteration\\$D=#1$}
+            \caption{\nth{2} Iteration}
         \end{subfigure}%
@@
             \includegraphics[width=1\linewidth]{images/fb/anim_d#1_i2.png}
-            \caption{\nth{3} Iteration\\$D=#1$}
+            \caption{\nth{3} Iteration}
         \end{subfigure}%
@@
 
-Node are distributed over the $K=10$ communities as shown in the histogram in Figure \ref{fig:fb_emb_weights}:
+The nodes are distributed over the $K=10$ communities as shown in the histograms in Figure \ref{fig:fb_emb_weights}.
+Figure \ref{fig:fb_emb_weights_d2} shows that with representation size $D=2$, ComE BGMM+VI drops 6 communites, effecitvelly using only 4 communities in the final embedding, because the two-dimensional node embeddings are not expressive enough to support more communities.
+Figures \ref{fig:fb_emb_weights_d4} and \ref{fig:fb_emb_weights_d128} show that with representation sizes $D=4$ and $D=128$ respectivelly, all $K=10$ communities are used.
+
+The tradeoff between the representation size of the embedding $D$ and the embedding expressiveness is demonstrated.
+When choosing a too low-dimensional embedding, the embedding might not be expressive enough to capture the communities and reduces the quality of the community embedding and detection.
+When choosing a too high-dimensional embedding, the node embeddings get so expressive that BGMM+VI is not able to drop unused communities because all communities are used in one of the many dimensions.
 
@@
 
-Figure \ref{fig:fb_emb_weights_d2} shows that with representation size $D=2$, ComE BGMM+VI drops 6 communites, effecitvelly using only 4 communities in the final embedding, because the two-dimensional node embeddings are not expressive enough to support more communities.
-Figures \ref{fig:fb_emb_weights_d4} and \ref{fig:fb_emb_weights_d128} show that with representation sizes $D=4$ and $D=128$ respectivelly, all $K=10$ communities are used.
+\subsection{Friend Suggestions}
+
+With node and community embeddings and community assignments generated for $D \in [2,4,128]$ and $K=10$ with training data in the previous section, top-$N$ friend suggestion recommendations are generated from the training node and community embeddings with Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com}.
+
+The shortest-embeddings-distance approach is employed, recommending friends to users that have the shortest distance node embeddings over all users (Algorithm \ref{alg:friend_sug}) or only over users in the same community (Algorithm \ref{alg:friend_sug_com}).
+Users who are already connected are not recommended again.
+
+\section{Evaluation}
+
+The charts in Fig. \ref{fig:fb_hit_rates} show the hit-rates for top-$N$ recommendations for testing users.
+
+\begin{figure}[h]
+    \centering
+    % d2
+    \begin{subfigure}{.48\textwidth}
+        \centering
+        \includegraphics[width=1\linewidth]{images/fb/hit_rates_d-2.png}
+        \caption{$D=2$ on linear $N$-axis.}
+        \label{fig:fb_hit_rates_d2}
+    \end{subfigure}%
+
+    % d4
+    \begin{subfigure}{.48\textwidth}
+        \centering
+        \includegraphics[width=1\linewidth]{images/fb/hit_rates_d-4.png}
+        \caption{$D=4$ on linear $N$-axis.}
+        \label{fig:fb_hit_rates_d4}
+    \end{subfigure}%
+
+    % d128
+    \begin{subfigure}{.48\textwidth}
+        \centering
+        \includegraphics[width=1\linewidth]{images/fb/hit_rates_d-128.png}
+        \caption{$D=128$ on linear $N$-axis.}
+        \label{fig:fb_hit_rates_d128}
+    \end{subfigure}%
+
+    \caption{Hit-rates of \citetitle{social_circles_fb} graph's top-$N$ friend suggestions on $N$-axis for $D \in [2,4,128]$.
+Hit-rate lines for Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} overlap for $D=2$ and $D=4$.}
+    \label{fig:fb_hit_rates}
+\end{figure}
+
+Two hit-rate lines are shown for each embedding representation size $D \in [2,4,128]$ on $N$-axis.
+The blue line shows the hit-rates when generating friend suggestions from all users (Algorithm \ref{alg:friend_sug}).
+The orange line shows the hit-rate when generating recommendations from users in the same community (Algorithm \ref{alg:friend_sug_com}).
+For lower-dimensional embeddings with $D \in [2,4]$, the hit-rates for Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} largely overlap.
+
+Table \ref{table:fb_hit_rates} shows readings of hit-rates over the algorithms and embedding dimensionality for top-$5$, top-$10$, and top-$20$ recommendations:
+
+\begin{figure}[h]
+    \centering
+    \caption{Hit-rates of \citetitle{social_circles_fb} graph's top-$N$ friend suggestions for algorithms \ref{alg:friend_sug} and \ref{alg:friend_sug_com}, $N \in [10, 20]$, and $D \in [2,4,128]$.}
+    \label{table:fb_hit_rates}
+    \begin{tabular}{ l | l | c | c | c }
+        \hline
+        \empty                                              & \empty  & top-$5$         & top-$10$        & top-$20$        \\
+        \hline
+        \hline
+        \multirow{3}{*}{Algorithm \ref{alg:friend_sug}}     & $D=2$   & 8.5\%           & 14.2\%          & 21.9\%          \\
+                                                            & $D=4$   & 18.1\%          & 26.5\%          & 38.4\%          \\
+                                                            & $D=128$ & \textbf{31.3\%} & \textbf{43.6\%} & \textbf{58.8\%} \\
+        \hline
+        \multirow{3}{*}{Algorithm \ref{alg:friend_sug_com}} & $D=2$   & 8.4\%           & 14.1\%          & 21.8\%          \\
+                                                            & $D=4$   & 18.0\%          & 26.4\%          & 38.2\%          \\
+                                                            & $D=128$ & \textbf{24.1\%} & \textbf{32.9\%} & \textbf{41.8\%} \\
+        \hline
+    \end{tabular}
+\end{figure}
+
+Hit-rates based on top-$5$, top-$10$, and top-$20$ recommendations are chosen since higher $N$ are not practical for recommendations.
+
+Presenting only the top-$10$ friend suggestions to users, a hit-rate of $43.6\%$ when considering all users, or $32.9\%$, when considering only users from the same community, is achieved.
+A top-$5$ hit-rate of $31.3\%$ (all users) and $24.1\%$ (same community) is achieved, which can be considered viable for business use-cases, especially for only showing 5 recommendations to users.
+A top-$20$ hit-rate of $58.8\%$ (all users) and $41.8\%$ (same community) adds to the presented results.
+
+\section{Conclusion}
+
+The proposed shortest-embedding-distance friend suggestion recommender system based on embeddings generated with the community embeddings algorithm ComE BGMM+VI shows promising results.
+A top-$10$ recommendations hit-rate of $43.6\%$ when considering all users (Algorithm \ref{alg:friend_sug}), and over $32.9\%$ when considering users in the same community (Algorithm \ref{alg:friend_sug_com}) is achieved for Facebook friend suggestions.
+
+\subsection{Future Work}
+
+This work explores generating friend suggestions from node and community embeddings generated by ComE.
+Three values of the representation size $D$ were used in experimentation.
+Experimenting with more, different combinations of hyperparameters, and especially varying the number of communities $K$ might be of interest.
+Since in this paper, friend suggestions were explored, it is left for future work to explore item-based recommendations using embeddings.
+More community-centric recommendations, which deeply consider the community embeddings in generating recommendations, are left for future work.
 

### 2020-10-12 paper-ffs.tex
rename paper to paper-ffs
replace social_circles_fb title and Figure->Fig.

--- 2020-10-12 conference_101719.tex
@@
 
+\usepackage{cite}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{commath}
+\usepackage{caption}
 \usepackage{subcaption}
 \usepackage[super]{nth}
-\usepackage[style=numeric, backend=bibtex, language=english, maxbibnames=99]{biblatex}
 
@@
 \emergencystretch=8em
-
-\bibliography{literature}
 
@@
 \begin{IEEEkeywords}
-    graph, embedding, community embedding, ComE, recommendations, friend suggestions
+    graph, embedding, community embedding, ComE, recommender systems, friend suggestions
 \end{IEEEkeywords}
@@
 
-\begin{figure}
+\begin{figure}[htbp]
     \centering
     \includegraphics[width=0.48\textwidth]{images/fb/graph_d4.png}
-    \caption{\citetitle{social_circles_fb} graph plotted with networkx's spring layout and node colors representing community membership obtained by ComE BGMM+VI with $D=4$.\cite{networkx}}
+    \caption{Social circles Facebook graph plotted with networkx's spring layout and node colors representing community membership obtained by ComE BGMM+VI with $D=4$ \cite{networkx}.}
     \label{fig:fb_graph}
@@
 
-\begin{figure}[h]
+\begin{figure}[htbp]
     \centering
@@
 
-\begin{figure}
+\begin{figure}[htbp]
     \centering
@@
 
-As can be seen in Figure \ref{fig:karateclub_spring}, the two communities in the \citetitle{KarateClubDS} dataset are correctly identified, despite the number of communities being initialized with $K=5$.
+As can be seen in Fig.
+\ref{fig:karateclub_spring}, the two communities in the \citetitle{KarateClubDS} dataset are correctly identified, despite the number of communities being initialized with $K=5$.
 Thanks to the Bayesian approach to community modeling and optimization through variational inference, three unused communities are dropped, which leaves the prominent two communities present in the dataset.
@@
 The top-$N$ friend suggestions, generated for the testing users with Algorithm \ref{alg:friend_sug_com}, are evaluated against the three removed test edges.
-The ranked lists of friend-suggestions shown in Figure \ref{tab:karateclub_emb_dists} is used to determine top-$N$ friend suggestions for each testing user and evaluate the recommendations my the hit-rate metric.
+The ranked lists of friend-suggestions shown in Fig.
+\ref{tab:karateclub_emb_dists} is used to determine top-$N$ friend suggestions for each testing user and evaluate the recommendations my the hit-rate metric.
 The LOO-testing edges are printed bold in Table \ref{tab:karateclub_emb_dists}.
@@
 The recommender system based on community embeddings with the Bayesian Gaussian mixture model and variational inference is quantitatively evaluated.
-Friend suggestions are generated for the \citetitle{social_circles_fb} dataset \cite{social_circles_fb, social_circles_in_ego_networks}.
+Friend suggestions are generated for the Social circles Facebook dataset \cite{social_circles_fb, social_circles_in_ego_networks}.
 
-The method of generating friend suggestions using ComE BGMM+VI embeddings and the smallest-distance approach is applied to the \citetitle{social_circles_fb} graph.
+The method of generating friend suggestions using ComE BGMM+VI embeddings and the smallest-distance approach is applied to the Social circles Facebook graph.
 Both Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} are evaluated.
@@
 
-The \citetitle{social_circles_fb} dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \citetitle{social_circles_in_ego_networks}.\cite{social_circles_in_ego_networks}
+The Social circles Facebook dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \citetitle{social_circles_in_ego_networks}.\cite{social_circles_in_ego_networks}
 
@@
 
-The \citetitle{social_circles_fb} graph is split into training and testing parts.
+The Social circles Facebook graph is split into training and testing parts.
 For evaluation, the leave-one-out (LOO) method is used, where for each testing user one edge is left out, then if the left out edge is in the user's top-$N$ recommendations, a hit is counted, otherwise, a miss is recorded.
@@
 
-$1169$ of the 4039 users of the \citetitle{social_circles_fb} graph have at least $50$ connections and are used for testing friend suggestions.
+$1169$ of the 4039 users of the Social circles Facebook graph have at least $50$ connections and are used for testing friend suggestions.
 The threshold of $50$ friends for considering users for testing is set to make sure enough data is available to make sensable suggestions for testing users.
@@
 
-Community embeddings for the \citetitle{social_circles_fb} graph are generated by running ComE BGMM+VI with the hyperparameters listed in Table \ref{tab:params_fb}.
+Community embeddings for the Social circles Facebook graph are generated by running ComE BGMM+VI with the hyperparameters listed in Table \ref{tab:params_fb}.
 
@@
     \centering
-    \caption{Hyperparameters used for the \citetitle{social_circles_fb} dataset.}
+    \caption{Hyperparameters used for the Social circles Facebook dataset.}
     \label{tab:params_fb}
@@
 A representation size $D \in [2,4,128]$ is chosen to determine the effect of the embedding's dimensionality on friend suggestions.
-It is hypothesized, that two dimensions are not sufficient to capture the structure of the \citetitle{social_circles_fb} graph, due to its size, therefore higher dimensional embeddings are evaluated as well.
+It is hypothesized, that two dimensions are not sufficient to capture the structure of the Social circles Facebook graph, due to its size, therefore higher dimensional embeddings are evaluated as well.
 
@@
 The $4$- and $128$-dimensional node and community embeddings cannot effectively be plotted in two-dimensional print.
-Instead, in Figures \ref{fig:fb_emb_anim_d4} and \ref{fig:fb_emb_anim_d128} the two first dimensions of the node and community embeddings are plotted to gain a narrow perspective on the resulting node embeddings.
+Instead, in Fig.
+\ref{fig:fb_emb_anim_d4} and Fig.
+\ref{fig:fb_emb_anim_d128} the two first dimensions of the node and community embeddings are plotted to gain a narrow perspective on the resulting node embeddings.
 
 \newcommand{\fbEmbAnimD}[1]{
-    \begin{figure*}
+    \begin{figure*}[htbp]
         \centering
@@
 Fig.
-\ref{fig:fb_graphs} shows the graph spring plotted with networkx and nodes colored by community membership after the lastest iteration of ComE.\cite{networkx} The spring plotted graph structure on Figure \ref{fig:fb_graphs} suggest, that with embedding dimension $D=4$, more fitting communities are detected than for $D=2$ and $D=128$.
+\ref{fig:fb_graphs} shows the graph spring plotted with networkx and nodes colored by community membership after the lastest iteration of ComE.\cite{networkx} The spring plotted graph structure on Fig.
+\ref{fig:fb_graphs} suggest, that with embedding dimension $D=4$, more fitting communities are detected than for $D=2$ and $D=128$.
 
-\begin{figure*}
+\begin{figure*}[htbp]
     \centering
@@
 
-Figure \ref{fig:fb_emb_anim_d2} shows node and community embeddings with representation size $D=2$.
-The limiting two-dimensional space does not allow ComE to represent the \citetitle{social_circles_fb} graph's structure sufficiently to utilize the $K=10$ components of the Gaussian mixture model.
+Fig.
+\ref{fig:fb_emb_anim_d2} shows node and community embeddings with representation size $D=2$.
+The limiting two-dimensional space does not allow ComE to represent the Social circles Facebook graph's structure sufficiently to utilize the $K=10$ components of the Gaussian mixture model.
 Only three components are used after the last of three iterations.
 
-While Figures \ref{fig:fb_emb_anim_d4} and \ref{fig:fb_emb_anim_d128} show only the first two dimensions, of the node embedding of 4 or 128 dimensionality respectively, the general structure of communities is visible.
+While Fig.
+\ref{fig:fb_emb_anim_d4} and Fig.
+\ref{fig:fb_emb_anim_d128} show only the first two dimensions, of the node embedding of 4 or 128 dimensionality respectively, the general structure of communities is visible.
 The development of the node embeddings over the three iterations shows the manifestation of the first-, second-, and higher-order proximity by ComE's closed loop.
@@
 
-The nodes are distributed over the $K=10$ communities as shown in the histograms in Figure \ref{fig:fb_emb_weights}.
-Figure \ref{fig:fb_emb_weights_d2} shows that with representation size $D=2$, ComE BGMM+VI drops 6 communites, effecitvelly using only 4 communities in the final embedding, because the two-dimensional node embeddings are not expressive enough to support more communities.
-Figures \ref{fig:fb_emb_weights_d4} and \ref{fig:fb_emb_weights_d128} show that with representation sizes $D=4$ and $D=128$ respectivelly, all $K=10$ communities are used.
+The nodes are distributed over the $K=10$ communities as shown in the histograms in Fig.
+\ref{fig:fb_emb_weights}.
+Fig.
+\ref{fig:fb_emb_weights_d2} shows that with representation size $D=2$, ComE BGMM+VI drops 6 communites, effecitvelly using only 4 communities in the final embedding, because the two-dimensional node embeddings are not expressive enough to support more communities.
+Fig.
+\ref{fig:fb_emb_weights_d4} and Fig.
+\ref{fig:fb_emb_weights_d128} show that with representation sizes $D=4$ and $D=128$ respectivelly, all $K=10$ communities are used.
 
@@
 
-\begin{figure*}
+\begin{figure*}[htbp]
     \centering
@@
 
-    \caption{Hit-rates of \citetitle{social_circles_fb} graph's top-$N$ friend suggestions on $N$-axis for $D \in [2,4,128]$.
+    \caption{Hit-rates of Social circles Facebook graph's top-$N$ friend suggestions on $N$-axis for $D \in [2,4,128]$.
 Hit-rate lines for Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} overlap for $D=2$ and $D=4$.}
@@
 
-\begin{figure}[h]
+\begin{figure}[htbp]
     \centering
-    \caption{Hit-rates of \citetitle{social_circles_fb} graph's top-$N$ friend suggestions for algorithms \ref{alg:friend_sug} and \ref{alg:friend_sug_com}, $N \in [10, 20]$, and $D \in [2,4,128]$.}
+    \caption{Hit-rates of Social circles Facebook graph's top-$N$ friend suggestions for algorithms \ref{alg:friend_sug} and \ref{alg:friend_sug_com}, $N \in [10, 20]$, and $D \in [2,4,128]$.}
     \label{table:fb_hit_rates}
@@
 %%% Bibliography
-\printbibliography
+\bibliographystyle{IEEEtran}
+\bibliography{literature}
 

### 2020-10-12 paper-ffs.tex
use IEEEtranN
for more cite… support
https://tex.stackexchange.com/questions/201582/natbib-ieeetran-and-alphanumeric-citation-is-there-an-ieeetransan-style-availa
\citetitle -> \citet

@@
 \usepackage{cite}
+\usepackage[numbers]{natbib}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 It returns the node embedding $\Phi$, context embedding $\Phi'$, community assignment $\Pi$, and community embedding $(\Psi,\Sigma)$.
-ComE BGMM+VI is based on the ComE algorithm presented by \citeauthor{ComE} in their paper \citetitle{ComE} as algorithm 1 on page 381 of the publication's in-proceeding \cite{ComE}.
+ComE BGMM+VI is based on the ComE algorithm presented by \citeauthor{ComE} in their paper \citet{ComE} as algorithm 1 on page 381 of the publication's in-proceeding \cite{ComE}.
 ComE BGMM+VI takes a Bayesian approach to community embedding by utilizing  a Bayesian Gaussian mixture model (BGMM) and variational inference (VI) for community embedding and detection instead of a non-Bayesian Gaussian mixture model (GMM) with expectation maximization (EM) \cite{ComE_BGMM_GH}.
@@
 
-The small \citetitle{KarateClubDS} dataset will be used to visually underline the motivation for using node embedding and community memberships generated by ComE BGMM+VI for generating friend suggestions for person nodes on the karate club graph \cite{KarateClubDS}.
+The small \citet{KarateClubDS} dataset will be used to visually underline the motivation for using node embedding and community memberships generated by ComE BGMM+VI for generating friend suggestions for person nodes on the karate club graph \cite{KarateClubDS}.
 
@@
     \includegraphics[width=0.4\textwidth]{images/karateclub/spring.png}
-    \caption{\citetitle{KarateClubDS} plotted with networkx's spring layout \cite{KarateClubDS, networkx}.}
+    \caption{\citet{KarateClubDS} plotted with networkx's spring layout \cite{KarateClubDS, networkx}.}
     \label{fig:karateclub_spring}
@@
 Fig.
-\ref{fig:karateclub_spring} shows the 34 nodes and 78 edges of the \citetitle{KarateClubDS} dataset plotted as a graph with the Python network package networkx's spring layout.\cite{networkx} Spring layout simulates a force-directed representation of the network, by treating edges as springs pulling nodes together and treating nodes as repelling objects, sometimes called an anti-gravity force.\cite{networkx} The node classification, represented by node color, shown in Fig.
+\ref{fig:karateclub_spring} shows the 34 nodes and 78 edges of the \citet{KarateClubDS} dataset plotted as a graph with the Python network package networkx's spring layout.\cite{networkx} Spring layout simulates a force-directed representation of the network, by treating edges as springs pulling nodes together and treating nodes as repelling objects, sometimes called an anti-gravity force.\cite{networkx} The node classification, represented by node color, shown in Fig.
 \ref{fig:karateclub_spring} was obtained by running ComE with BGMM and VI with the hyperparameters presented in Table \ref{tab:params_karateclub}.
@@
 As can be seen in Fig.
-\ref{fig:karateclub_spring}, the two communities in the \citetitle{KarateClubDS} dataset are correctly identified, despite the number of communities being initialized with $K=5$.
+\ref{fig:karateclub_spring}, the two communities in the \citet{KarateClubDS} dataset are correctly identified, despite the number of communities being initialized with $K=5$.
 Thanks to the Bayesian approach to community modeling and optimization through variational inference, three unused communities are dropped, which leaves the prominent two communities present in the dataset.
@@
 
-\citetitle{KarateClubDS} is split into training and testing parts.
+\citet{KarateClubDS} is split into training and testing parts.
 For evaluation, the leave-one-out (LOO) method is used, where for each testing user one edge is left out, then if the left out edge is in the user's top-$N$ recommendations, a hit is counted, otherwise, a miss is recorded.
@@
     \includegraphics[width=1\linewidth]{images/karateclub/embeddings_5.png}
-    \caption{\citetitle{KarateClubDS} training dataset node and community embedding and node classification.}
+    \caption{\citet{KarateClubDS} training dataset node and community embedding and node classification.}
     \label{fig:karateclub_emb}
@@
     \includegraphics[width=.4\textwidth]{images/karateclub/hit_rates.png}
-    \caption{Hit-rates from top-$N$ recommendations on \citetitle{KarateClubDS}.}
+    \caption{Hit-rates from top-$N$ recommendations on \citet{KarateClubDS}.}
     \label{fig:karateclub_hitrates}
@@
 Fig.
-\ref{fig:karateclub_hitrates} shows promising results for using ComE to generate top-$N$ friend suggestions on the small \citetitle{KarateClubDS}.
+\ref{fig:karateclub_hitrates} shows promising results for using ComE to generate top-$N$ friend suggestions on the small \citet{KarateClubDS}.
 The achieved hit-rate starts at 33\% for $N=1$, reaches 67\% at $N=3$, and maxes out at 100\% for $N=7$; therefore, when presenting three friend suggestions to one test user, at least in $66\%$ of cases a friend suggestion would be of interest.
@@
 
-The Social circles Facebook dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \citetitle{social_circles_in_ego_networks}.\cite{social_circles_in_ego_networks}
+The Social circles Facebook dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \citet{social_circles_in_ego_networks}.\cite{social_circles_in_ego_networks}
 
@@
 %%% Bibliography
-\bibliographystyle{IEEEtran}
+\bibliographystyle{IEEEtranN}
 \bibliography{literature}

### 2020-10-12 paper-ffs.tex
oh yea, citet, then ok
https://tex.stackexchange.com/questions/202963/how-to-cite-author-in-ieee-format

@@
     \includegraphics[width=0.48\textwidth]{images/fb/graph_d4.png}
-    \caption{Social circles Facebook graph plotted with networkx's spring layout and node colors representing community membership obtained by ComE BGMM+VI with $D=4$ \cite{networkx}.}
+    \caption{\citet{social_circles_fb} graph plotted with networkx's spring layout and node colors representing community membership obtained by ComE BGMM+VI with $D=4$ \cite{networkx}.}
     \label{fig:fb_graph}
@@
 The recommender system based on community embeddings with the Bayesian Gaussian mixture model and variational inference is quantitatively evaluated.
-Friend suggestions are generated for the Social circles Facebook dataset \cite{social_circles_fb, social_circles_in_ego_networks}.
+Friend suggestions are generated for the \citet{social_circles_fb} dataset \cite{social_circles_fb, social_circles_in_ego_networks}.
 
-The method of generating friend suggestions using ComE BGMM+VI embeddings and the smallest-distance approach is applied to the Social circles Facebook graph.
+The method of generating friend suggestions using ComE BGMM+VI embeddings and the smallest-distance approach is applied to the \citet{social_circles_fb} graph.
 Both Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} are evaluated.
@@
 
-The Social circles Facebook dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \citet{social_circles_in_ego_networks}.\cite{social_circles_in_ego_networks}
+The \citet{social_circles_fb} dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \citet{social_circles_in_ego_networks}.\cite{social_circles_in_ego_networks}
 
@@
 
-The Social circles Facebook graph is split into training and testing parts.
+The \citet{social_circles_fb} graph is split into training and testing parts.
 For evaluation, the leave-one-out (LOO) method is used, where for each testing user one edge is left out, then if the left out edge is in the user's top-$N$ recommendations, a hit is counted, otherwise, a miss is recorded.
@@
 
-$1169$ of the 4039 users of the Social circles Facebook graph have at least $50$ connections and are used for testing friend suggestions.
+$1169$ of the 4039 users of the \citet{social_circles_fb} graph have at least $50$ connections and are used for testing friend suggestions.
 The threshold of $50$ friends for considering users for testing is set to make sure enough data is available to make sensable suggestions for testing users.
@@
 
-Community embeddings for the Social circles Facebook graph are generated by running ComE BGMM+VI with the hyperparameters listed in Table \ref{tab:params_fb}.
+Community embeddings for the \citet{social_circles_fb} graph are generated by running ComE BGMM+VI with the hyperparameters listed in Table \ref{tab:params_fb}.
 
@@
     \centering
-    \caption{Hyperparameters used for the Social circles Facebook dataset.}
+    \caption{Hyperparameters used for the \citet{social_circles_fb} dataset.}
     \label{tab:params_fb}
@@
 A representation size $D \in [2,4,128]$ is chosen to determine the effect of the embedding's dimensionality on friend suggestions.
-It is hypothesized, that two dimensions are not sufficient to capture the structure of the Social circles Facebook graph, due to its size, therefore higher dimensional embeddings are evaluated as well.
+It is hypothesized, that two dimensions are not sufficient to capture the structure of the \citet{social_circles_fb} graph, due to its size, therefore higher dimensional embeddings are evaluated as well.
 
@@
 \ref{fig:fb_emb_anim_d2} shows node and community embeddings with representation size $D=2$.
-The limiting two-dimensional space does not allow ComE to represent the Social circles Facebook graph's structure sufficiently to utilize the $K=10$ components of the Gaussian mixture model.
+The limiting two-dimensional space does not allow ComE to represent the \citet{social_circles_fb} graph's structure sufficiently to utilize the $K=10$ components of the Gaussian mixture model.
 Only three components are used after the last of three iterations.
@@
 
-    \caption{Hit-rates of Social circles Facebook graph's top-$N$ friend suggestions on $N$-axis for $D \in [2,4,128]$.
+    \caption{Hit-rates of \citet{social_circles_fb} graph's top-$N$ friend suggestions on $N$-axis for $D \in [2,4,128]$.
 Hit-rate lines for Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} overlap for $D=2$ and $D=4$.}
@@
     \centering
-    \caption{Hit-rates of Social circles Facebook graph's top-$N$ friend suggestions for algorithms \ref{alg:friend_sug} and \ref{alg:friend_sug_com}, $N \in [10, 20]$, and $D \in [2,4,128]$.}
+    \caption{Hit-rates of \citet{social_circles_fb} graph's top-$N$ friend suggestions for algorithms \ref{alg:friend_sug} and \ref{alg:friend_sug_com}, $N \in [10, 20]$, and $D \in [2,4,128]$.}
     \label{table:fb_hit_rates}

### 2020-10-12 paper-ffs.tex
Tom's feedback

@@
     Recommender systems are used in a wide range of business applications and are essential for online, e-business models to survive and strive in the contemporary market.
-Using graph embeddings for recommendation tasks, have the possibility of improving upon recommender systems, because of data compression, their feature vector format, and sub-quadratic time complexity.
+Using graph embeddings for recommendation tasks has the possibility of improving upon recommender systems, because of data compression, the feature vector format, and sub-quadratic time complexity on computing embeddings.
     Graph and community embeddings generated with ComE BGMM+VI are used to build a recommender system for friend suggestions.
@@
     Recommendations are evaluated by the top-N hit-rate over users with at least 50 friends.
-A friend suggestions recommender system with a top-10 leave-one-out hit-rate of 43.6\% and run-time optimized 32.9\% is presented.
+A friend suggestions recommender system with a top-10 leave-one-out hit-rate of 43.6\% and run-time optimized hit-rate of 32.9\% is presented.
 \end{abstract}
@@
 Most contemporary technology companies heavily rely on recommender systems to drive usage of their services and consumption of their content.
-Users, in turn, rely on recommender systems to find what they want and need and save searching time.
+Users, in turn, rely on recommender systems to find what they want, need, save searching time, and what they might not have found otherwise.
 State-of-the-art recommender systems provide a competitive advantage desperately needed by online services.
@@
 The ranked lists of friend-suggestions shown in Fig.
-\ref{tab:karateclub_emb_dists} is used to determine top-$N$ friend suggestions for each testing user and evaluate the recommendations my the hit-rate metric.
+\ref{tab:karateclub_emb_dists} are used to determine top-$N$ friend suggestions for each testing user and evaluate the recommendations my the hit-rate metric.
 The LOO-testing edges are printed bold in Table \ref{tab:karateclub_emb_dists}.
@@
 Fig.
-\ref{fig:fb_emb_weights_d2} shows that with representation size $D=2$, ComE BGMM+VI drops 6 communites, effecitvelly using only 4 communities in the final embedding, because the two-dimensional node embeddings are not expressive enough to support more communities.
+\ref{fig:fb_emb_weights_d2} shows that with representation size $D=2$, ComE BGMM+VI drops 6 communities, effecitvelly using only 4 communities in the final embedding, because the two-dimensional node embeddings are not expressive enough to support more communities.
 Fig.

### 2020-10-12 paper-ffs.tex
fix bib formatting of urls
feedback from @Elli-cyber
thx ❤️

@@
 \usepackage[super]{nth}
+\usepackage{url}
+
+\def\UrlBreaks{\do\/\do-}
 
@@
 
-Graphs, such as social networks, knowledge graphs, content-rating graphs, and communication networks, emerge naturally from various real-world situations.
+Graphs, such as social networks, knowledge graphs, content-rating graphs, and communication networks emerge naturally from various real-world situations.
 Analyzing these graphs leads to findings and understanding of the underlying structures, coherences, and dependencies.
-Recently, methods for embedding graph's nodes into lower-dimensional Euclidean spaces, called graph embeddings, have gained traction in multiple areas of data science research \cite{Goyal_2018}.
+Recently, methods for embedding graph's nodes into lower-dimensional, Euclidean spaces, called graph embeddings, have gained traction in multiple areas of data science research \cite{Goyal_2018}.
 
 Due to the rapid growth of the internet and data accumulation, recommender systems are essential for e-business and online business models to survive and strive in the contemporary market \cite{Polatidis2013RecommenderST}.
-Modern recommender systems need to take into account the huge amounts of user data generated at all times in big data systems around the world and improve recommendations instead of failing under the thrust of big data overload.
+Modern recommender systems need to take into account the huge amounts of data generated at all times in big data systems around the world and improve recommendations instead of failing under the thrust of big data overload.
 
-Utilizing graph embeddings for recommendation tasks, has recently gained research traction \cite{Palumbo2018AnEC, Palumbo2018KnowledgeGE, GradGyenge2017GraphEB, Sathish2019GraphEB}.
-The advantages of graph embeddings include data compression and the Euclidean feature vector format \cite{Godec2018}.
+Utilizing graph embeddings for recommendation tasks, has recently gained research interest \cite{Palumbo2018AnEC, Palumbo2018KnowledgeGE, GradGyenge2017GraphEB, Sathish2019GraphEB}.
+The advantages of graph embeddings include data compression and the feature vector format \cite{Godec2018}.
 Given these advantages and provided competitive results, graph embeddings have the possibility of greatly improving upon graph-based use-cases like recommender systems.
@@
 Friend suggestions are a simpler type of recommender system.
-For friend suggestions, no distinction is made between users and items.
+For friend suggestions no distinction is made between users and items.
 The entity user is both the subject and object of recommendation.
@@
 The graph of users and friendships is embedded to a lower-dimensional space with the community embedding algorithm ComE BGMM+VI \cite{ComE, ComE+, ComE_BGMM_GH}.
-The approach can be considered a variant of collaborative filtering with the euclidean distance of user embeddings and user community membership as measures for user similarity.
+The approach can be considered a variant of collaborative filtering with the Euclidean distance of user embeddings and user community membership as measures for user similarity.
 The proposed advantage of using such an approach is that community embeddings optimize first-, second-, and higher-order proximity between users in the node embedding.
@@
 Utilizing the top-$N$ approach with hit-rate to evaluate recommender systems is advantageous to evaluating recommender systems by a link prediction approach since the top-$N$ approach is more realistic in comparison to actual recommender system use-cases.
-When you open Netflix, Amazon, YouTube, or Facebook friend suggestions, one or multiple top-$N$ recommendation lists are generated and displayed.
+When you open Netflix, Amazon, YouTube, or Facebook one or multiple top-$N$ recommendation lists are generated and displayed.
 If you click on an item and buy, watch, or befriend, that is considered a hit, otherwise, a miss.
 
-The hit-rate metric on top-$N$ recommendations provides a realistic option of evaluating recommender systems and with the leave-one-out (LOO) strategy is used often in literature \cite{Cremonesi2010PerformanceOR, Palumbo2017entity2rec, Zhao2019ATS, He2017NeuralCF}.
+The hit-rate metric on top-$N$ recommendations provides a realistic option of evaluating recommender systems and is often used with the leave-one-out (LOO) strategy in literature \cite{Cremonesi2010PerformanceOR, Palumbo2017entity2rec, Zhao2019ATS, He2017NeuralCF}.
 
@@
     \centering
-    \caption{Algorithm \ref{alg:friend_sug} and \ref{alg:friend_sug_com} time complexity.}
+    \caption{Time complexity of algorithms \ref{alg:friend_sug} and \ref{alg:friend_sug_com}.}
     \label{tab:runtimes}
@@
 For each testing user, a ranked list of non-friend users from the same community is generated (Algorithm \ref{alg:friend_sug_com}).
-A test user's friend suggestion list is ordered in ascending order by the euclidean distance between the node embeddings.
+A test user's friend suggestion list is ordered in ascending order by the Euclidean distance between the node embeddings.
 Table \ref{tab:karateclub_emb_dists} shows the test users' friend suggestion ranked lists.
@@
 The top-$N$ friend suggestions, generated for the testing users with Algorithm \ref{alg:friend_sug_com}, are evaluated against the three removed test edges.
-The ranked lists of friend-suggestions shown in Fig.
-\ref{tab:karateclub_emb_dists} are used to determine top-$N$ friend suggestions for each testing user and evaluate the recommendations my the hit-rate metric.
+The ranked lists of friend-suggestions shown in Table \ref{tab:karateclub_emb_dists} are used to determine top-$N$ friend suggestions for each testing user and evaluate the recommendations my the hit-rate metric.
 The LOO-testing edges are printed bold in Table \ref{tab:karateclub_emb_dists}.
@@
 Fig.
-\ref{fig:fb_graphs} shows the graph spring plotted with networkx and nodes colored by community membership after the lastest iteration of ComE.\cite{networkx} The spring plotted graph structure on Fig.
+\ref{fig:fb_graphs} shows the graph spring plotted with networkx and nodes colored by community membership after the last iteration of ComE.\cite{networkx} The spring plotted graph structure on Fig.
 \ref{fig:fb_graphs} suggest, that with embedding dimension $D=4$, more fitting communities are detected than for $D=2$ and $D=128$.

### 2020-10-12 paper-ffs.tex
typo

@@
 
-Table \ref{table:fb_hit_rates} shows readings of hit-rates over the algorithms and embedding dimensionality for top-$5$, top-$10$, and top-$20$ recommendations:
+Table \ref{tab:fb_hit_rates} shows readings of hit-rates over the algorithms and embedding dimensionality for top-$5$, top-$10$, and top-$20$ recommendations:
 
@@
     \centering
-    \caption{Hit-rates of \citet{social_circles_fb} graph's top-$N$ friend suggestions for algorithms \ref{alg:friend_sug} and \ref{alg:friend_sug_com}, $N \in [10, 20]$, and $D \in [2,4,128]$.}
-    \label{table:fb_hit_rates}
+    \caption{Hit-rates of \citet{social_circles_fb} graph's top-$N$ friend suggestions for algorithms \ref{alg:friend_sug} and \ref{alg:friend_sug_com}, $N \in [5, 10, 20]$, and $D \in [2, 4, 128]$.}
+    \label{tab:fb_hit_rates}
     \begin{tabular}{ l | l | c | c | c }

### 2020-10-12 paper-ffs.tex

@@
 A top-$10$ recommendations hit-rate of $43.6\%$ when considering all users (Algorithm \ref{alg:friend_sug}), and over $32.9\%$ when considering users in the same community (Algorithm \ref{alg:friend_sug_com}) is achieved for Facebook friend suggestions.
+Both results were achieved with a representation size $D=128$.
+Lower hit-rates are obtained for $D=2$ and $D=4$.
+See Table \ref{tab:fb_hit_rates}.
+
+Algorithm \ref{alg:friend_sug} achieves the better hit-rate in comparison to Algorithm \ref{alg:friend_sug_com}, since all users are considered for embedding instead of just users of the same community.
+Algorithm \ref{alg:friend_sug_com}, on the other hand, has better time complexity than Algorithm \ref{alg:friend_sug}, since only users in the same community are considered for friend suggestions instead of all users.
+Algorithm \ref{alg:friend_sug_com} is scalable to larger datasets if the number of communities $K$ can be considered to scale with the graph size $(\abs{V}, \abs{E})$.
 

### 2020-10-12 paper-ffs.tex
add facebook to title
add HSE tranks
from ProfPPanfilov
natbib does not have a citetitle
citet cites last name of first author, or similar

@@
 \documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
 
@@
 \usepackage{graphicx}
-\usepackage{textcomp}
+\usepackage[warn]{textcomp}
 \usepackage{multirow}
@@
 
-\title{Community Embeddings for Friend Suggestions}
+\title{Community Embeddings for Facebook Friend Suggestions\\
+    \thanks{The reported study was partially supported by RFBR grant \textnumero 20-07-00958. The paper was prepared within the framework of the HSE University Project Group Competition 2020-2022.}
+}
 
@@
     \includegraphics[width=0.48\textwidth]{images/fb/graph_d4.png}
-    \caption{\citet{social_circles_fb} graph plotted with networkx's spring layout and node colors representing community membership obtained by ComE BGMM+VI with $D=4$ \cite{networkx}.}
+    \caption{\textit{Social circles: Facebook} graph plotted with networkx's spring layout and node colors representing community membership obtained by ComE BGMM+VI with $D=4$ \cite{networkx}.}
     \label{fig:fb_graph}
@@
 It returns the node embedding $\Phi$, context embedding $\Phi'$, community assignment $\Pi$, and community embedding $(\Psi,\Sigma)$.
-ComE BGMM+VI is based on the ComE algorithm presented by \citeauthor{ComE} in their paper \citet{ComE} as algorithm 1 on page 381 of the publication's in-proceeding \cite{ComE}.
+ComE BGMM+VI is based on the ComE algorithm presented by \citeauthor{ComE} in their paper \textit{Learning Community Embedding with Community Detection and Node Embedding on Graphs} as algorithm 1 on page 381 of the publication's in-proceeding \cite{ComE}.
 ComE BGMM+VI takes a Bayesian approach to community embedding by utilizing  a Bayesian Gaussian mixture model (BGMM) and variational inference (VI) for community embedding and detection instead of a non-Bayesian Gaussian mixture model (GMM) with expectation maximization (EM) \cite{ComE_BGMM_GH}.
@@
 
-The small \citet{KarateClubDS} dataset will be used to visually underline the motivation for using node embedding and community memberships generated by ComE BGMM+VI for generating friend suggestions for person nodes on the karate club graph \cite{KarateClubDS}.
+The small \textit{Zachary’s Karate Club graph} dataset will be used to visually underline the motivation for using node embedding and community memberships generated by ComE BGMM+VI for generating friend suggestions for person nodes on the karate club graph \cite{KarateClubDS}.
 
@@
     \includegraphics[width=0.4\textwidth]{images/karateclub/spring.png}
-    \caption{\citet{KarateClubDS} plotted with networkx's spring layout \cite{KarateClubDS, networkx}.}
+    \caption{\textit{Zachary’s Karate Club graph} plotted with networkx's spring layout \cite{KarateClubDS, networkx}.}
     \label{fig:karateclub_spring}
@@
 Fig.
-\ref{fig:karateclub_spring} shows the 34 nodes and 78 edges of the \citet{KarateClubDS} dataset plotted as a graph with the Python network package networkx's spring layout.\cite{networkx} Spring layout simulates a force-directed representation of the network, by treating edges as springs pulling nodes together and treating nodes as repelling objects, sometimes called an anti-gravity force.\cite{networkx} The node classification, represented by node color, shown in Fig.
+\ref{fig:karateclub_spring} shows the 34 nodes and 78 edges of the \textit{Zachary’s Karate Club graph} dataset plotted as a graph with the Python network package networkx's spring layout.\cite{networkx} Spring layout simulates a force-directed representation of the network, by treating edges as springs pulling nodes together and treating nodes as repelling objects, sometimes called an anti-gravity force.\cite{networkx} The node classification, represented by node color, shown in Fig.
 \ref{fig:karateclub_spring} was obtained by running ComE with BGMM and VI with the hyperparameters presented in Table \ref{tab:params_karateclub}.
@@
 As can be seen in Fig.
-\ref{fig:karateclub_spring}, the two communities in the \citet{KarateClubDS} dataset are correctly identified, despite the number of communities being initialized with $K=5$.
+\ref{fig:karateclub_spring}, the two communities in the \textit{Zachary’s Karate Club graph} dataset are correctly identified, despite the number of communities being initialized with $K=5$.
 Thanks to the Bayesian approach to community modeling and optimization through variational inference, three unused communities are dropped, which leaves the prominent two communities present in the dataset.
@@
 
-\citet{KarateClubDS} is split into training and testing parts.
+\textit{Zachary’s Karate Club graph} is split into training and testing parts.
 For evaluation, the leave-one-out (LOO) method is used, where for each testing user one edge is left out, then if the left out edge is in the user's top-$N$ recommendations, a hit is counted, otherwise, a miss is recorded.
@@
     \includegraphics[width=1\linewidth]{images/karateclub/embeddings_5.png}
-    \caption{\citet{KarateClubDS} training dataset node and community embedding and node classification.}
+    \caption{\textit{Zachary’s Karate Club graph} training dataset node and community embedding and node classification.}
     \label{fig:karateclub_emb}
@@
     \includegraphics[width=.4\textwidth]{images/karateclub/hit_rates.png}
-    \caption{Hit-rates from top-$N$ recommendations on \citet{KarateClubDS}.}
+    \caption{Hit-rates from top-$N$ recommendations on \textit{Zachary’s Karate Club graph}.}
     \label{fig:karateclub_hitrates}
@@
 Fig.
-\ref{fig:karateclub_hitrates} shows promising results for using ComE to generate top-$N$ friend suggestions on the small \citet{KarateClubDS}.
+\ref{fig:karateclub_hitrates} shows promising results for using ComE to generate top-$N$ friend suggestions on the small \textit{Zachary’s Karate Club graph}.
 The achieved hit-rate starts at 33\% for $N=1$, reaches 67\% at $N=3$, and maxes out at 100\% for $N=7$; therefore, when presenting three friend suggestions to one test user, at least in $66\%$ of cases a friend suggestion would be of interest.
@@
 The recommender system based on community embeddings with the Bayesian Gaussian mixture model and variational inference is quantitatively evaluated.
-Friend suggestions are generated for the \citet{social_circles_fb} dataset \cite{social_circles_fb, social_circles_in_ego_networks}.
+Friend suggestions are generated for the \textit{Social circles: Facebook} dataset \cite{social_circles_fb, social_circles_in_ego_networks}.
 
-The method of generating friend suggestions using ComE BGMM+VI embeddings and the smallest-distance approach is applied to the \citet{social_circles_fb} graph.
+The method of generating friend suggestions using ComE BGMM+VI embeddings and the smallest-distance approach is applied to the \textit{Social circles: Facebook} graph.
 Both Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} are evaluated.
@@
 
-The \citet{social_circles_fb} dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \citet{social_circles_in_ego_networks}.\cite{social_circles_in_ego_networks}
+The \textit{Social circles: Facebook} dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \textit{Learning to Discover Social Circles in Ego Networks}.\cite{social_circles_in_ego_networks}
 
@@
 
-The \citet{social_circles_fb} graph is split into training and testing parts.
+The \textit{Social circles: Facebook} graph is split into training and testing parts.
 For evaluation, the leave-one-out (LOO) method is used, where for each testing user one edge is left out, then if the left out edge is in the user's top-$N$ recommendations, a hit is counted, otherwise, a miss is recorded.
@@
 
-$1169$ of the 4039 users of the \citet{social_circles_fb} graph have at least $50$ connections and are used for testing friend suggestions.
+$1169$ of the 4039 users of the \textit{Social circles: Facebook} graph have at least $50$ connections and are used for testing friend suggestions.
 The threshold of $50$ friends for considering users for testing is set to make sure enough data is available to make sensable suggestions for testing users.
@@
 
-Community embeddings for the \citet{social_circles_fb} graph are generated by running ComE BGMM+VI with the hyperparameters listed in Table \ref{tab:params_fb}.
+Community embeddings for the \textit{Social circles: Facebook} graph are generated by running ComE BGMM+VI with the hyperparameters listed in Table \ref{tab:params_fb}.
 
@@
     \centering
-    \caption{Hyperparameters used for the \citet{social_circles_fb} dataset.}
+    \caption{Hyperparameters used for the \textit{Social circles: Facebook} dataset.}
     \label{tab:params_fb}
@@
 A representation size $D \in [2,4,128]$ is chosen to determine the effect of the embedding's dimensionality on friend suggestions.
-It is hypothesized, that two dimensions are not sufficient to capture the structure of the \citet{social_circles_fb} graph, due to its size, therefore higher dimensional embeddings are evaluated as well.
+It is hypothesized, that two dimensions are not sufficient to capture the structure of the \textit{Social circles: Facebook} graph, due to its size, therefore higher dimensional embeddings are evaluated as well.
 
@@
 \ref{fig:fb_emb_anim_d2} shows node and community embeddings with representation size $D=2$.
-The limiting two-dimensional space does not allow ComE to represent the \citet{social_circles_fb} graph's structure sufficiently to utilize the $K=10$ components of the Gaussian mixture model.
+The limiting two-dimensional space does not allow ComE to represent the \textit{Social circles: Facebook} graph's structure sufficiently to utilize the $K=10$ components of the Gaussian mixture model.
 Only three components are used after the last of three iterations.
@@
 
-    \caption{Hit-rates of \citet{social_circles_fb} graph's top-$N$ friend suggestions on $N$-axis for $D \in [2,4,128]$.
+    \caption{Hit-rates of \textit{Social circles: Facebook} graph's top-$N$ friend suggestions on $N$-axis for $D \in [2,4,128]$.
 Hit-rate lines for Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} overlap for $D=2$ and $D=4$.}
@@
     \centering
-    \caption{Hit-rates of \citet{social_circles_fb} graph's top-$N$ friend suggestions for algorithms \ref{alg:friend_sug} and \ref{alg:friend_sug_com}, $N \in [5, 10, 20]$, and $D \in [2, 4, 128]$.}
+    \caption{Hit-rates of \textit{Social circles: Facebook} graph's top-$N$ friend suggestions for algorithms \ref{alg:friend_sug} and \ref{alg:friend_sug_com}, $N \in [5, 10, 20]$, and $D \in [2, 4, 128]$.}
     \label{tab:fb_hit_rates}

### 2020-10-14 paper-ffs.tex
feedback

@@
 Algorithm \ref{alg:friend_sug_com} describes in pseudocode how recommendations are computed from ComE BGMM+VI node and community embeddings and community assignments.
-The advantage of also considers community membership, is that an improvement in time complexity can be obtained, by considering only users in the same community for friend suggestions.
+The advantage of also considering community membership, is that an improvement in time complexity can be obtained, by considering only users in the same community for friend suggestions.
 
@@
 
-The runtimes for Algorithm \ref{alg:friend_sug} and \ref{alg:friend_sug_com} when considering $K$ as constant or scaling w.r.t the graph $G = (V, E)$ are shown in Table \ref{tab:runtimes}.
-The number of friend suggestions $N$ is considered constant w.r.t the graph $G = (V, E)$.
+The runtimes for Algorithm \ref{alg:friend_sug} and \ref{alg:friend_sug_com} when considering $K$ as constant or scaling w.r.t.
+the graph $G = (V, E)$ are shown in Table \ref{tab:runtimes}.
+The number of friend suggestions $N$ is considered constant w.r.t.
+the graph $G = (V, E)$.
 
@@
 
-When the hyperparameter number of communities $K$ is considered non-constant with respect to the graph $G$, Algorithm \ref{alg:friend_sug_com} reduces the quadratic runtime in comparison to Algorithm \ref{alg:friend_sug_com}.
+When the hyperparameter number of communities $K$ is considered scaling w.r.t.
+the graph $G$'s size $(\abs{V}, \abs{E})$, Algorithm \ref{alg:friend_sug_com} reduces the quadratic runtime in comparison to Algorithm \ref{alg:friend_sug}.
 $K$ can therefore reduce the quadratic summand $\abs{V}^2N$ by only considering users of the same community for friend suggestions.
@@
 Fig.
-\ref{fig:karateclub_spring} shows the 34 nodes and 78 edges of the \textit{Zachary’s Karate Club graph} dataset plotted as a graph with the Python network package networkx's spring layout.\cite{networkx} Spring layout simulates a force-directed representation of the network, by treating edges as springs pulling nodes together and treating nodes as repelling objects, sometimes called an anti-gravity force.\cite{networkx} The node classification, represented by node color, shown in Fig.
+\ref{fig:karateclub_spring} shows the 34 nodes and 78 edges of the \textit{Zachary’s Karate Club graph} dataset plotted as a graph with the Python network package networkx's spring layout \cite{networkx}.
+Spring layout simulates a force-directed representation of the network, by treating edges as springs pulling nodes together and treating nodes as repelling objects, sometimes called an anti-gravity force \cite{networkx}.
+The node classification, represented by node color, shown in Fig.
 \ref{fig:karateclub_spring} was obtained by running ComE with BGMM and VI with the hyperparameters presented in Table \ref{tab:params_karateclub}.
@@
 Thanks to the Bayesian approach to community modeling and optimization through variational inference, three unused communities are dropped, which leaves the prominent two communities present in the dataset.
-The node classification obtained reflects the node classification published in the \citeyear{ComE} original ComE paper by \citeauthor{ComE}.\cite{ComE}
+The node classification obtained reflects the node classification published in the \citeyear{ComE} original ComE paper by \citeauthor{ComE} \cite{ComE}.
 
@@
 
-The \textit{Social circles: Facebook} dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \textit{Learning to Discover Social Circles in Ego Networks}.\cite{social_circles_in_ego_networks}
+The \textit{Social circles: Facebook} dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \textit{Learning to Discover Social Circles in Ego Networks} \cite{social_circles_in_ego_networks}.
 
@@
 Now that the testing users are identified, the leave-one-out method is employed for obtaining one testing friendship per testing user.
-The friendship chosen to leave out for testing for each testing user is chosen randomly using NumPy's random choice.\cite{oliphant2006guide, van2011numpy}
+The friendship chosen to leave out for testing for each testing user is chosen randomly using NumPy's random choice \cite{oliphant2006guide, van2011numpy}.
 
@@
 Fig.
-\ref{fig:fb_graphs} shows the graph spring plotted with networkx and nodes colored by community membership after the last iteration of ComE.\cite{networkx} The spring plotted graph structure on Fig.
+\ref{fig:fb_graphs} shows the graph spring plotted with networkx and nodes colored by community membership after the last iteration of ComE \cite{networkx}.
+The spring plotted graph structure on Fig.
 \ref{fig:fb_graphs} suggest, that with embedding dimension $D=4$, more fitting communities are detected than for $D=2$ and $D=128$.

### 2020-10-14 paper-ffs.tex
feedback Opa

@@
 
-The small \textit{Zachary’s Karate Club graph} dataset will be used to visually underline the motivation for using node embedding and community memberships generated by ComE BGMM+VI for generating friend suggestions for person nodes on the karate club graph \cite{KarateClubDS}.
+The small \textit{Zachary’s Karate Club graph} dataset will be used to visually underline the motivation for using node embedding and community memberships generated by ComE BGMM+VI for generating friend suggestions for person nodes on the Karate Club graph \cite{KarateClubDS}.
 
@@
 The top-$N$ friend suggestions, generated for the testing users with Algorithm \ref{alg:friend_sug_com}, are evaluated against the three removed test edges.
-The ranked lists of friend-suggestions shown in Table \ref{tab:karateclub_emb_dists} are used to determine top-$N$ friend suggestions for each testing user and evaluate the recommendations my the hit-rate metric.
+The ranked lists of friend-suggestions shown in Table \ref{tab:karateclub_emb_dists} are used to determine top-$N$ friend suggestions for each testing user and evaluate the recommendations by the hit-rate metric.
 The LOO-testing edges are printed bold in Table \ref{tab:karateclub_emb_dists}.

### 2020-10-14 paper-ffs.tex
Social circles: Facebook -> Social Circles: Facebook
feedback Opa

@@
     \includegraphics[width=0.48\textwidth]{images/fb/graph_d4.png}
-    \caption{\textit{Social circles: Facebook} graph plotted with networkx's spring layout and node colors representing community membership obtained by ComE BGMM+VI with $D=4$ \cite{networkx}.}
+    \caption{\textit{Social Circles: Facebook} graph plotted with networkx's spring layout and node colors representing community membership obtained by ComE BGMM+VI with $D=4$ \cite{networkx}.}
     \label{fig:fb_graph}
@@
 The recommender system based on community embeddings with the Bayesian Gaussian mixture model and variational inference is quantitatively evaluated.
-Friend suggestions are generated for the \textit{Social circles: Facebook} dataset \cite{social_circles_fb, social_circles_in_ego_networks}.
+Friend suggestions are generated for the \textit{Social Circles: Facebook} dataset \cite{social_circles_fb, social_circles_in_ego_networks}.
 
-The method of generating friend suggestions using ComE BGMM+VI embeddings and the smallest-distance approach is applied to the \textit{Social circles: Facebook} graph.
+The method of generating friend suggestions using ComE BGMM+VI embeddings and the smallest-distance approach is applied to the \textit{Social Circles: Facebook} graph.
 Both Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} are evaluated.
@@
 
-The \textit{Social circles: Facebook} dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \textit{Learning to Discover Social Circles in Ego Networks} \cite{social_circles_in_ego_networks}.
+The \textit{Social Circles: Facebook} dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \textit{Learning to Discover Social Circles in Ego Networks} \cite{social_circles_in_ego_networks}.
 
@@
 
-The \textit{Social circles: Facebook} graph is split into training and testing parts.
+The \textit{Social Circles: Facebook} graph is split into training and testing parts.
 For evaluation, the leave-one-out (LOO) method is used, where for each testing user one edge is left out, then if the left out edge is in the user's top-$N$ recommendations, a hit is counted, otherwise, a miss is recorded.
@@
 
-$1169$ of the 4039 users of the \textit{Social circles: Facebook} graph have at least $50$ connections and are used for testing friend suggestions.
+$1169$ of the 4039 users of the \textit{Social Circles: Facebook} graph have at least $50$ connections and are used for testing friend suggestions.
 The threshold of $50$ friends for considering users for testing is set to make sure enough data is available to make sensable suggestions for testing users.
@@
 
-Community embeddings for the \textit{Social circles: Facebook} graph are generated by running ComE BGMM+VI with the hyperparameters listed in Table \ref{tab:params_fb}.
+Community embeddings for the \textit{Social Circles: Facebook} graph are generated by running ComE BGMM+VI with the hyperparameters listed in Table \ref{tab:params_fb}.
 
@@
     \centering
-    \caption{Hyperparameters used for the \textit{Social circles: Facebook} dataset.}
+    \caption{Hyperparameters used for the \textit{Social Circles: Facebook} dataset.}
     \label{tab:params_fb}
@@
 A representation size $D \in [2,4,128]$ is chosen to determine the effect of the embedding's dimensionality on friend suggestions.
-It is hypothesized, that two dimensions are not sufficient to capture the structure of the \textit{Social circles: Facebook} graph, due to its size, therefore higher dimensional embeddings are evaluated as well.
+It is hypothesized, that two dimensions are not sufficient to capture the structure of the \textit{Social Circles: Facebook} graph, due to its size, therefore higher dimensional embeddings are evaluated as well.
 
@@
 \ref{fig:fb_emb_anim_d2} shows node and community embeddings with representation size $D=2$.
-The limiting two-dimensional space does not allow ComE to represent the \textit{Social circles: Facebook} graph's structure sufficiently to utilize the $K=10$ components of the Gaussian mixture model.
+The limiting two-dimensional space does not allow ComE to represent the \textit{Social Circles: Facebook} graph's structure sufficiently to utilize the $K=10$ components of the Gaussian mixture model.
 Only three components are used after the last of three iterations.
@@
 
-    \caption{Hit-rates of \textit{Social circles: Facebook} graph's top-$N$ friend suggestions on $N$-axis for $D \in [2,4,128]$.
+    \caption{Hit-rates of \textit{Social Circles: Facebook} graph's top-$N$ friend suggestions on $N$-axis for $D \in [2,4,128]$.
 Hit-rate lines for Algorithm \ref{alg:friend_sug} and Algorithm \ref{alg:friend_sug_com} overlap for $D=2$ and $D=4$.}
@@
     \centering
-    \caption{Hit-rates of \textit{Social circles: Facebook} graph's top-$N$ friend suggestions for algorithms \ref{alg:friend_sug} and \ref{alg:friend_sug_com}, $N \in [5, 10, 20]$, and $D \in [2, 4, 128]$.}
+    \caption{Hit-rates of \textit{Social Circles: Facebook} graph's top-$N$ friend suggestions for algorithms \ref{alg:friend_sug} and \ref{alg:friend_sug_com}, $N \in [5, 10, 20]$, and $D \in [2, 4, 128]$.}
     \label{tab:fb_hit_rates}

### 2020-10-14 paper-ffs.tex
feedback
Opa

@@
 The spring plotted graph structure on Fig.
-\ref{fig:fb_graphs} suggest, that with embedding dimension $D=4$, more fitting communities are detected than for $D=2$ and $D=128$.
+\ref{fig:fb_graphs} suggests, that with embedding dimension $D=4$, more fitting communities are detected than for $D=2$ and $D=128$.
 
@@
 
-The shortest-embeddings-distance approach is employed, recommending friends to users that have the shortest distance node embeddings over all users (Algorithm \ref{alg:friend_sug}) or only over users in the same community (Algorithm \ref{alg:friend_sug_com}).
+The shortest-embeddings-distance approach is employed, recommending friends to users who have the shortest distance node embeddings over all users (Algorithm \ref{alg:friend_sug}) or only over users in the same community (Algorithm \ref{alg:friend_sug_com}).
 Users who are already connected are not recommended again.

### 2020-10-14 paper-ffs.tex
figure1 should be on page 1

@@
     Graphs, such as social networks, emerge naturally from various real-world situations. Recently, graph embedding methods have gained traction in data science research.
-    Recommender systems are used in a wide range of business applications and are essential for online, e-business models to survive and strive in the contemporary market.
-Using graph embeddings for recommendation tasks has the possibility of improving upon recommender systems, because of data compression, the feature vector format, and sub-quadratic time complexity on computing embeddings.
+    Recommender systems are used in a wide range of business applications and are essential for online e-business models to survive and strive in the contemporary market.
+Using graph embeddings for recommendation tasks can improve upon recommender systems because of data compression, the feature vector format, and sub-quadratic time complexity on computing embeddings.
     Graph and community embeddings generated with ComE BGMM+VI are used to build a recommender system for friend suggestions.
@@
 ComE BGMM+VI applies a Bayesian Gaussian mixture model and variational inference for community embedding and detection.
-    Recommendations are evaluated by the top-N hit-rate over users with at least 50 friends.
+    Recommendations are evaluated by the top-N hit-rate for users with at least 50 friends.
 A friend suggestions recommender system with a top-10 leave-one-out hit-rate of 43.6\% and run-time optimized hit-rate of 32.9\% is presented.
@@
 
-Community Embeddings, in addition to embedding a graph's nodes through first- and second-order proximity, also preserve higher-order proximity by embedding clusters present in the graph data.
-The graph and community embedding algorithm ComE aims to preserve first-, second- and higher-order proximity by embedding a graph's nodes and communities \cite{ComE}.
-
-This work specifically examines community embeddings for friend suggestion recommender systems and evaluates recommendations on social network graph data for the use-case of friend suggestions.
-Graph and community embeddings generated with ComE BGMM+VI are used to develop a friend suggestions recommender system based on the shortest distances between nodes in the embedding.
-Recommendations are evaluated by the top-$N$ recommendations hit-rate of test edges.
-A friend suggestions recommender system with a top-10 leave-one-out hit-rate of 43.6\% and run-time optimized 32.9\% is presented.
-
 \begin{figure}[htbp]
@@
 \end{figure}
+
+Community Embeddings, in addition to embedding a graph's nodes through first- and second-order proximity, also preserve higher-order proximity by embedding clusters present in the graph data.
+The graph and community embedding algorithm ComE aims to preserve first-, second- and higher-order proximity by embedding a graph's nodes and communities \cite{ComE}.
+
+This work specifically examines community embeddings for friend suggestion recommender systems and evaluates recommendations on social network graph data for the use-case of friend suggestions.
+Graph and community embeddings generated with ComE BGMM+VI\footnote{The ComE BGMM+VI source code and the code used to generate friend suggestions is published at \url{https://github.com/abegehr/ComE_BGMM} \cite{ComE_BGMM_GH}.} are used to develop a friend suggestions recommender system based on the shortest distances between nodes in the embedding.
+Recommendations are evaluated by the top-$N$ recommendations hit-rate of test edges.
+A friend suggestions recommender system with a top-10 leave-one-out hit-rate of 43.6\% and run-time optimized 32.9\% is presented.
 
